---
title: "Create Tuggerah Lakes EEC layer"
author: "Amy Whitehead"
date: "Wednesday, September 24, 2014"
output: html_document
---


```{r setup_functions}
# load packages and set working directory
  rm(list=ls())
  
  library(raster)
  library(rgdal)
  library(maptools)
  library(rgeos)

# set computer path
  computer <- "//654cw-20990/Amy"
#   computer <- "Z:/Amy"

```

```{r shpr2raster}
shp2raster <- function(shp, mask.raster, label, value, bkg = 0,transform = FALSE, proj.from = NA, proj.to = NA, map = TRUE, save=TRUE,mask=TRUE) {
  require(raster, rgdal)
  
  # use transform==TRUE if the polygon is not in the same coordinate system as
  # the output raster, setting proj.from & proj.to to the appropriate
  # projections
  if (transform == TRUE) {
    if(is.na(proj4string(shp))) proj4string(shp) <- proj.from
    shp <- spTransform(shp, proj.to)
  }
  
  # convert the shapefile to a raster based on a standardised background raster with 
  # 'value' as the areas where the shapefile are and 'bkg' representing the areas outside the polygon
  r <- rasterize(shp, mask.raster,field=value,background=bkg)
    # mask out areas outside the boundary of the mask raster
    if(mask==T) r <- mask(r,mask.raster)
  
  # save a copy of the raster as a tif in the working directory
  if(save==TRUE) writeRaster(r, filename = label, format = "GTiff",overwrite = T)
    
  # plot map of new raster
  if (map == TRUE) plot(r, main = label, axes = F, box = F)
  
  names(r) <- label
  return(r)
}

```

```{r Tuggerah Lakes EEC}
# wyong clipping mask
  wyong.clipping.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/wyong.clipping.mask.tif"))

# Load Tuggerah Lakes shapefiles
  tuggerah.lakes <- readShapePoly("//654cw-20990/Amy/GIS_data/Wyong/Wyong Shire Council Data/Species/TuggerahLakesSaltmarsh(EEC)_WSC_20140716.shp",proj4string=GDA94.56)
  tuggerah.lakes.dist <- readShapePoly("//654cw-20990/Amy/GIS_data/Wyong/Wyong Shire Council Data/Species/TuggerahLakesSaltmarshDisturbedZone(EEC)_WSC_20140716.shp",proj4string=GDA94.56)

# buffer polygons & convert to rasters
  tuggerah.lakes.mask <- shp2raster(gBuffer(tuggerah.lakes,width=100),wyong.clipping.mask,value=1,bkg=0,label="TuggerahLakesSaltmarsh(EEC)_WSC_20140716",save=F)
  tuggerah.lakes.dist.mask <- shp2raster(gBuffer(tuggerah.lakes.dist,width=100),wyong.clipping.mask,value=0.5,bkg=0,label="TuggerahLakesSaltmarshDisturbedZone(EEC)_WSC_20140716",save=F)

# sum polygons
  tuggerah.lakes.combined <- sum(tuggerah.lakes.mask,tuggerah.lakes.dist.mask)
    # set distrubed zone to a lower value
    tuggerah.lakes.combined[tuggerah.lakes.combined==1.5] <- 0.5 
  
  writeRaster(tuggerah.lakes.combined,paste0(computer,"/GIS_data/Hunter/zonation/wyong/Tuggerah_Lakes_Saltmarsh_EEC.tif"),overwrite=T)