Identify species with points in LHSA
========================================================

# Species
1. Check for Maxent species that have points within the Greater Hunter
2. Clip the extant distribution for species with at least 1 point in the GH
3. Compare the clipped LH species distributions with the GH distribution and replace species where the LH.max or AUC value is below the thresholda with a presence-absence raster
4. Create Presence-absence rasters for all point species

# TECs
5. Check TECS that have points in the LH
6. Clip the extant distribution of TECS with at least 1 point in the LH
7. Compare the clipped LH TEC distributions with the GH distribution and replace species where the LH.max is below the threshold with a presence-absence raster
8. Create Presence-absence rasters for all point tecs

9. Clip all pre1750 SDMs to LH based on the extant LH SDMs that have been retained.

10. Check that all layers are the same dimensions

11. Create spp files


```{r}
rm(list=ls())

library(raster)


#computer <- "~" #My computer
computer <- "Z:/Amy" #Super computer
# computer <- "//654cw-20990/Amy"

# clip pre1750 layers?
  pre1750 <- TRUE
  clip <- FALSE

# directories
  maxent.dir <- paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/all_variables/output/")

# location of GH files
  GH.zonation.dir <- paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/")

# location of GH files
  GH_PM.zonation.dir <- paste0(computer,"/GIS_data/Hunter/zonation/GH_PM/")

# set projections
  GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

# GH masks
  GH.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/GH.mask.tif"))
  GH.clipping.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/GH.clipping.mask_v2.tif"))

# open species list
  protected.species <- read.csv(paste0(computer,"/GIS_data/Hunter/species point data/IBRA threatened species list.csv"))

# delete all existing tifs in greater hunter folder
## only run this if you definitely want to delete these files!!
# tifs <- dir(paste0(GH_PM.zonation.dir,"extant/"), pattern="GH_PM.tif$",full.names=T)
# file.remove(tifs)


maxent.summary <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/all_variables/output/GH DotE report - maxent summary.csv"))

poorly.modelled <- read.csv(paste0(maxent.dir,"DotE report - poorly modelled species.csv"))

```

```{r presence.absence.raster function}
    
presence.absence.raster <- function (mask.raster,species.data,raster.label="") {
    #set the cells that contain points to 1
  speciesRaster <- rasterize(species.data,mask.raster,field=1)
    if(cellStats(speciesRaster,max)>0){
    speciesRaster <- mask(merge(speciesRaster,mask.raster),mask.raster)
    #label the raster
    names(speciesRaster) <- gsub(" ","_",raster.label)
    writeRaster(speciesRaster,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/extant/",raster.label,"_SSI.GH.tif"), format="GTiff",overwrite=T)
  cat("Converted",as.character(raster.label),"to raster","\n")
  }
  gc()
}

```

Clip species

```{r identify maxent species within HCCREMS}
# import maxent point data for GH data
  maxent.data <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/species_data/maxent.data_ALA.NSW.csv"))
#     colnames(maxent.data) <- c("easting","northing","species")

# create list of unique MaxEnt species
  me.species <- data.frame(species=as.character(unique(maxent.summary$Species)),AUC=NA,in.GH=NA,in.HCCREMS=NA,GH.max=NA,HCCREMS.max=NA)
    

# loop through each species, identify which has points in HCCREMS and return list
  for(i in seq(me.species$species)){
    s <- maxent.data[as.character(maxent.data$species)==me.species$species[i],]
    
    # identify points within region
    me.species$AUC[i] <- maxent.summary$Test.AUC[grepl(me.species$species[i],maxent.summary$Species)]
    me.species$in.GH[i] <- nrow(s)
    protected.species$GH_PM[protected.species$Scientific.Name==as.character(me.species$species[i])] <- me.species$in.GH[i]
    in.HCCREMS <- length(which(!is.na(extract(GH.clipping.mask,s[,c("easting","northing")]))))
    
    
    if(in.HCCREMS>0) {
      me.species$in.HCCREMS[i] <- "TRUE"
      cat(as.character(me.species$species[i]),"has", in.HCCREMS, "points in GH region","\n")
      protected.species$greater.hunter[protected.species$Scientific.Name==as.character(me.species$species[i])] <- in.HCCREMS
        } else me.species$in.HCCREMS[i] <- "FALSE"
  }

```

```{r clip maxent output for species with points in GH}

# create list of HCCREMS species to clip
  GH.tifs <- me.species$species[me.species$in.HCCREMS == TRUE & me.species$AUC>=0.7]
    GH.tifs <- gsub(" ","_",GH.tifs)

clip.to.GH <- function (asc.file) {
    r <- raster(asc.file)
    species <- gsub("_SDM.GH_PM.tif|Z:/Amy/GIS_data/Hunter/zonation/GH_PM/extant/","",asc.file)
    
    r <- mask(crop(r,GH.mask),GH.mask)
    
    if(length(species[grepl("pre1750",species)])==1) {
      writeRaster(r,paste0(GH.zonation.dir,"pre1750/",as.character(species),"_SDM.GH.tif"), overwrite=T,datatype="INT2U")
      } else {
        r <- mask(r,GH.clipping.mask)
        writeRaster(r,paste0(GH.zonation.dir,"extant/",as.character(species),"_SDM.GH.tif"), overwrite=T,datatype="INT2U")
      }  
    cat(" converted",as.character(species), "to tif","\n")
    #file.remove(paste0(maxent.dir,asc.file))
  }

  for(j in seq(GH.tifs)){  
    species <- GH.tifs[j] 
      species <- gsub("_"," ",species)  
    
    tryCatch({
      clip.to.GH(paste0(GH_PM.zonation.dir,"extant/",GH.tifs[j],"_SDM.GH_PM.tif"))
      me.species[me.species$species==as.character(species),"GH.max"] <- cellStats(raster(paste0(GH_PM.zonation.dir,"extant/",GH.tifs[j],"_SDM.GH_PM.tif"),crs=GDA94.56),max)/1000
      me.species[me.species$species==as.character(species),"HCCREMS.max"] <- cellStats(raster(paste0(GH.zonation.dir,"extant/",GH.tifs[j],"_SDM.GH.tif"),crs=GDA94.56),max)/1000
      
      if(me.species[me.species$species==as.character(species),"GH.max"]*1000 > 1){
        protected.species$GH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SDM"
      }
    }, error=function(err) cat(""),warning=function(war) cat("Check",GH.tifs[j],"for missing tif","\n"))
  }

# save species list output for future use
  write.csv(me.species,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/maxent_species.list.csv"),row.names=F)

```

```{r identify species with low AUC scores in LH and convert to SSI}
me.species <- read.csv(paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/maxent_species.list.csv"))

# set minimum threshold
  threshold <- 0.7

# identify species that have low SDM values within the LH
  species.list <- as.character(me.species$species[me.species$HCCREMS.max/me.species$GH.max<0.25])
    species.list <- species.list[!is.na(species.list)]
  # add those species that seem to be missing SDMs  
    species.list <- unique(c(as.character(species.list),as.character(me.species$species[me.species$in.HCCREMS==TRUE & is.na(me.species$HCCREMS.max) & me.species$in.HCCREMS<100]),as.character(me.species$species[me.species$AUC < threshold & me.species$in.HCCREMS<100])))
  
# create presence-absence rasters for species with low AUC values 
    if(length(species.list)>0){
     
      for(i in seq(species.list)){
        species <- gsub(" ","_",species.list[i])
        species.data <- maxent.data[maxent.data$species == species.list[i],]
        species.data <- species.data[,c("easting","northing")]
                presence.absence.raster(GH.clipping.mask,species.data, raster.label=species)
        try({
            file.remove(paste0(GH.zonation.dir,"extant/",species,"_SDM.GH.tif"))
            cat("Removed",paste0(species,"_SDM.GH.tif","\n"))
            },silent=T)
        species <- gsub("_"," ",species)
        protected.species$GH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SSI"
      }
    }

# remove species with poor AUC values & more than 100 points
species.list <- as.character(me.species$species[me.species$AUC < threshold & me.species$in.GH>100])
for(i in seq(species.list)){
try({
            file.remove(paste0(GH.zonation.dir,"extant/",gsub(" ","_",species.list[i]),"_SDM.GH.tif"))
            cat("Removed",paste0(species.list[i],"_SDM.GH.tif","\n"))
            protected.species$GH.sdm[protected.species$Scientific.Name==as.character(species.list[i])] <- "SDM removed"
            },silent=T)
}

# save species list output for future use
  write.csv(me.species,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/maxent_species.list.csv"),row.names=F)

```


```{r create species SSI tifs}
sdm.species <- gsub("_SDM.GH.tif","",dir(paste0(GH.zonation.dir,"extant/"), pattern="SDM.GH"))
  
  ssi.dir <- paste0(computer,"/GIS_data/Hunter/zonation/GH_PM/SSI/")

  ssi.species <- data.frame(species=dir(ssi.dir, pattern=".txt$"),in.GH=NA,in.HCCREMS=NA)
    ssi.species <- ssi.species[!grepl(paste0(sdm.species,collapse="|"),gsub(" ","_",gsub("_GH.PM.txt","",ssi.species$species))),]

for(i in seq(ssi.species$species)){
  try({
    species.data <- read.table(paste0(ssi.dir,ssi.species$species[i]),sep="\t")
    colnames(species.data) <- c("easting","northing","V3","V4")
  species <- strsplit(as.character(ssi.species$species[i]),"_GH.PM.txt")
    species <- gsub(" ","_",species)
  
  # identify points within region
    ssi.species$in.GH[i] <- nrow(species.data)
    in.HCCREMS <- length(which(!is.na(extract(GH.clipping.mask,species.data[,c("easting","northing")]))))
    
    species <- gsub("_"," ",species)
    protected.species$GH_PM[protected.species$Scientific.Name==as.character(species)] <- nrow(species.data)
    protected.species$GH_PM.sdm[protected.species$Scientific.Name==as.character(species)] <- "SSI"  
  
    if(in.HCCREMS>0) {
      ssi.species$in.HCCREMS[i] <- "TRUE"
      cat(as.character(species),"has",in.HCCREMS,"points in GH","\n")
          
      presence.absence.raster(GH.clipping.mask,species.data[,1:2], raster.label=species)
      
      protected.species$GH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SSI"
      protected.species$greater.hunter[protected.species$Scientific.Name==as.character(species)] <- in.HCCREMS
    
    } else ssi.species$in.HCCREMS[i] <- "FALSE"
  })
  
  }



write.csv(ssi.species,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/ssi.species.csv"),row.names=F)
# write.csv(protected.species,paste0(computer,"/GIS_data/Hunter/species point data/IBRA threatened species list.csv"),row.names=F)

```


Clip TECS

```{r identify maxent tec within HCCREMS}
# import maxent point data for GH data
  maxent.data <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/species_data/maxent.data_tecs.csv"))
   maxent.data$tec <- gsub("'",".",maxent.data$tec) 

  maxentResults <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/all_variables/output/tecs/pre1750v2/contributions.csv"))
    maxentResults$tec <- gsub("'",".",maxentResults$tec)

# create list of unique MaxEnt tec
  me.tec <- data.frame(tec=unique(maxent.data$tec),in.GH=NA,in.HCCREMS=NA,GH.max=NA,HCCREMS.max=NA,AUC=NA)

# loop through each tec, identify which has points in HCCREMS and return list
  for(i in seq(me.tec$tec)){
    s <- maxent.data[maxent.data$tec==me.tec$tec[i],]
    tec <- gsub("_"," ",me.tec$tec[i])
    
    # identify points within region
    me.tec$in.GH[i] <- nrow(s)
    protected.species$GH_PM[protected.species$Scientific.Name==as.character(tec)] <- me.tec$in.GH[i]
    in.HCCREMS <- length(which(!is.na(extract(GH.clipping.mask,s[,c("easting","northing")]))))
    
    if(in.HCCREMS>0) {
      me.tec$in.HCCREMS[i] <- "TRUE"
      cat(as.character(me.tec$tec[i]),"has", in.HCCREMS, "points in HCCREMS","\n")
      tec.data$GH.points[tec.data$TEC_Amy==as.character(me.tec$tec[i])] <- in.HCCREMS
      protected.species$greater_hunter[protected.species$Scientific.Name==as.character(tec)] <- in.HCCREMS
        } else me.tec$in.HCCREMS[i] <- "FALSE"
    me.tec$AUC[i] <- maxentResults[grepl(me.tec$tec[i],maxentResults$tec),"cv.roc.mean" ]
  }

```

```{r clip tec maxent output for tec with points in HCCREMS}
# create list of HCCREMS tec to clip
  GH.tifs <- me.tec$tec[me.tec$in.HCCREMS == TRUE]
    GH.tifs <- gsub(" ","_",GH.tifs)
    GH.tifs <- gsub("'",".",GH.tifs)

# function to clip to HCCREMS region
  clip.to.GH <- function(tiff, mask.raster){
    r <- raster(paste0(GH_PM.zonation.dir,"extant/",tiff,"_SDM.GH_PM.tif"))
    
    if( cellStats(r,max) > 1){
      r <- mask(crop(r,mask.raster),mask.raster,filename=paste0(GH.zonation.dir,"extant/",tiff,"_SDM.GH.tif"),format="GTiff",overwrite=T)
      cat("Clipped",as.character(tiff),"to Greater Hunter","\n")}
      
  }

  for(j in seq(GH.tifs)){  
    tec <- GH.tifs[j]  
    
    tryCatch({
      clip.to.GH(GH.tifs[j],GH.clipping.mask)
      me.tec[me.tec$tec==tec,"GH.max"] <- cellStats(raster(paste0(GH_PM.zonation.dir,"extant/",GH.tifs[j],"_SDM.GH_PM.tif")),max)/1000
      me.tec[me.tec$tec==tec,"HCCREMS.max"] <- cellStats(raster(paste0(GH.zonation.dir,"extant/",GH.tifs[j],"_SDM.GH.tif")),max)/1000
      protected.species$GH_PM.sdm[protected.species$Scientific.Name==as.character(gsub("_"," ",tec))] <- "SDM"
      
      if(me.tec[me.tec$tec==tec,"GH.max"]*1000 > 1){
        tec.data$HCCREMS.sdm[tec.data$TEC_Amy==as.character(tec)] <- "SDM"
        protected.species$GH.sdm[protected.species$Scientific.Name==as.character(gsub("_"," ",tec))] <- "SDM"
      }
    }, error=function(err) cat(""),warning=function(war) cat("Check",GH.tifs[j],"for missing tif","\n"))
  }

# save tec list output for future use
  write.csv(me.tec,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/maxent_tec.list.csv"),row.names=F)

```


```{r identify tec with low AUC scores in GH and convert to SSI}

# # set minimum threshold
  threshold <- 0.7

# identify tec that have low SDM values within the GH
  low.AUC <- me.tec$tec[me.tec$AUC < threshold]
    low.AUC <- as.character(low.AUC[!is.na(low.AUC)])
  low.predictions <- as.character(me.tec$tec[me.tec$HCCREMS.max/me.tec$GH.max<0.25])
    low.predictions <- as.character(low.predictions[!is.na(low.predictions)])
  missing.sdms <- as.character(me.tec$tec[me.tec$in.HCCREMS==TRUE & is.na(me.tec$GH.max)])
  # add those tec that seem to be missing SDMs  
    tec.list <- c(low.AUC,low.predictions,missing.sdms)
  
# create presence-absence rasters for tec with low SDM values 
    if(length(tec.list)>0){
     
      for(i in seq(tec.list)){
        tec <- gsub("_"," ",tec.list[i])
        
        ssi.data <- maxent.data[maxent.data$tec == tec.list[i],]
        ssi.data <- ssi.data[,c("easting","northing")]
        protected.species$GH_PM[protected.species$Scientific.Name==tec)] <- nrow(ssi.data)
        protected.species$GH_PM.sdm[protected.species$Scientific.Name==tec)] <- "SSI"
  
        presence.absence.raster(GH.clipping.mask,ssi.data, raster.label=tec.list[i])
        try({
            file.remove(paste0(GH.zonation.dir,"extant/",tec.list[i],"_SDM.GH.tif"))
            cat("Removed",paste0(tec.list[i],"_SDM.GH.tif","\n"))
            },silent=T)
        
        tec.data$HCCREMS.sdm[tec.data$TEC_Amy==as.character(tec.list[i])] <- "SSI"
      }
    }

# save tec list output for future use
  write.csv(me.tec,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/maxent_tec.list.csv"),row.names=F)

```


```{r create tec SSI tifs}

  ssi.dir <- paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/ssi_files/tecs/")

  ssi.tec <- data.frame(file.name=dir(ssi.dir, pattern=".txt$", recursive=T),in.GH=NA,in.HCCREMS=NA)
    ssi.tec$tec <- gsub("forestwoodland","forest_woodland",gsub("new_south_wales","nsw",gsub("bioregions","bioregion",gsub("_gh.txt","",tolower(ssi.tec$file.name)))))
  ssi.tecs <- setdiff(ssi.tec$tec,GH.tifs)
    ssi.tec <- ssi.tec[grepl(paste0(ssi.tecs,collapse="|"),ssi.tec$tec),]    

for(i in seq(ssi.tec$tec)){  
  ssi.data <- read.table(paste0(ssi.dir,ssi.tec$file.name[i]),sep=" ")
    colnames(ssi.data) <- c("easting","northing","V3","V4")
  tec <- ssi.tec$tec[i]
  
  # identify points within region
    ssi.tec$in.GH[i] <- nrow(ssi.data)
    protected.species$GH_PM[protected.species$Scientific.Name==gsub("_"," ",tec)] <- nrow(ssi.data)
    protected.species$GH_PM.sdm[protected.species$Scientific.Name==gsub("_"," ",tec)] <- "SSI"
    in.HCCREMS <- length(which(!is.na(extract(GH.clipping.mask,ssi.data[,c("easting","northing")]))))
    
    if(in.HCCREMS>0) {
      ssi.tec$in.HCCREMS[i] <- "TRUE"
      cat(as.character(tec),"has",in.HCCREMS,"points in greater hunter","\n")
          
#       presence.absence.raster(GH.clipping.mask,ssi.data[,c("easting","northing")], raster.label=tec)
      
      tec.data$HCCREMS.sdm[tec.data$TEC_Amy==tec] <- "SSI"
      tec.data$HCCREMS.points[tec.data$TEC_Amy==tec] <- in.HCCREMS
      
      protected.species$greater.hunter[protected.species$Scientific.Name==gsub("_"," ",tec)] <- in.HCCREMS
      protected.species$GH.sdm[protected.species$Scientific.Name==gsub("_"," ",tec)] <- "SSI"
    
    } else ssi.tec$in.HCCREMS[i] <- "FALSE"
  
  }

write.csv(ssi.tec,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/ssi.tec.csv"),row.names=F)

```

```{r clip pre1750 layers}
if (pre1750 == TRUE){

  cat("Clipping pre1750 layers to Greater Hunter","\n")
  
# function to clip to HCCREMS region
  clip.pre1750.to.GH <- function(tiff, mask.raster){
    r <- raster(paste0(GH_PM.zonation.dir,"pre1750/",tiff),crs=GDA94.56)
    tiff <- gsub(".GH_PM.tif","",tiff)
      r <- mask(crop(r,mask.raster),mask.raster,filename=paste0(LH.zonation.dir,"pre1750/",tiff,".GH.tif"),format="GTiff",overwrite=T)
      cat("Clipped",as.character(tiff),"to Greater Hunter","\n")
    }      
  
  
sdms <- dir(paste0(GH.zonation.dir,"extant/"),pattern="_SDM.GH.tif")
  sdms <- gsub("SDM.GH","pre1750_SDM.GH_PM",sdms)
  
    for(i in seq(sdms)){
      try(clip.pre1750.to.GH(sdms[i],GH.urban.clipping.mask),silent=T)
    }
}

# remove species with poor AUC values & more than 100 points
species.list <- gsub(" ","_",as.character(poorly.modelled$Species[poorly.modelled$N.records>100]))
for(i in seq(species.list)){
try({
            file.remove(paste0(GH.zonation.dir,"pre1750/",species.list[i],"_pre1750_SDM.GH.tif"))
            cat("Removed",paste0(species.list[i],"_pre1750_SDM.GH.tif","\n"))
            },silent=T)
}

```



```{r create zonation spp file}
  ignore.species <- gsub(" ","_",protected.species$Scientific.Name[protected.species$ignore=="Y"])

  extant.tifs <- dir(paste0(GH.zonation.dir,"extant/"), pattern=".GH.tif$")
    extant.tifs <- extant.tifs[!extant.tifs %in% paste0(ignore.species,"_SSI.GH.tif")]
    extant.tifs <- extant.tifs[!extant.tifs %in% paste0(ignore.species,"_SDM.GH.tif")]

duplicates <- extant.tifs[duplicated(gsub("_SSI.GH.tif|_SDM.GH.tif","",extant.tifs))]
    extant.tifs <- extant.tifs[!extant.tifs %in% duplicates]

#     extant.tifs <- extant.tifs[!grepl("Anthochaera_phrygia|Lathamus_discolor",extant.tifs)]
    extant.tifs <- paste0("extant/",extant.tifs)

GH.extant.zonation.spp <- data.frame(weight=1.0, alpha=1.0, bqp.row=1.0, bqp.buffer=1.0, cell.removal=1.0, species=extant.tifs )
  write.table(GH.extant.zonation.spp,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/GH.extant.zonation.spp"),sep="\t",row.names=FALSE, col.names=FALSE)

# LH.pre1750.zonation.spp <- data.frame(weight=1.0, alpha=1.0, bqp.row=1.0, bqp.buffer=1.0, cell.removal=1.0, species=pre1750.tifs )
#   write.table(LH.pre1750.zonation.spp,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/LH.pre1750.zonation.spp"),sep="\t",row.names=FALSE, col.names=FALSE)


weights <- protected.species[protected.species$ignore!="Y",c("Scientific.Name","weight")]
temp <- tec.data[!duplicated(tec.data$TEC_Amy),c("TEC_Amy","weight")]
  temp$TEC_Amy <- tolower(temp$TEC_Amy)
  colnames(temp) <- c("Scientific.Name","weight")
weights <- rbind(weights,temp)
  weights$Scientific.Name <- gsub("bioregions","bioregion",gsub(" ","_", weights$Scientific.Name))
  weights <- weights[!is.na(weights$weight),]

#species weights
for(i in seq(GH.extant.zonation.spp$species)){
  try(GH.extant.zonation.spp$weight[i] <- weights$weight[weights$Scientific.Name == gsub("extant|\\/|DotE|\\.GH|\\_GH|\\.tif|\\_SDM|\\_SSI","",GH.extant.zonation.spp$species[i])],silent=T)
}

GH.extant.zonation.spp$weight[is.na(GH.extant.zonation.spp$weight)] <- 1

write.table(GH.extant.zonation.spp,paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/GH.extant.zonation.weighted.spp"),sep="\t",row.names=FALSE, col.names=FALSE)

write.csv(protected.species,paste0(computer,"/GIS_data/Hunter/species point data/IBRA threatened species list.csv"),row.names=F)

write.csv(tec.data,paste0(computer,"/GIS_data/Hunter/species point data/GreaterHunter_DRAFT_100812 (2).csv"),row.names=F)


# file.remove(paste0(LH.zonation.dir,"extant/",gsub(" SDM","_SSI",gsub("_"," ",extant.tifs[duplicated(strip.names(extant.tifs))]))))
# file.rename(paste0(LH.zonation.dir,"extant/",extant.tifs),paste0(LH.zonation.dir,"extant/",gsub(" ","_",extant.tifs)))
```
