Add security categories to LH protected areas layer
========================================================

This RMarkdown script takes individual layers representing protected areas within the Lower Hunter valley, assigns a *security of protection* score.  The layers are then merged and exported as a clipped file for use in Zonation analyses.

I have built this from the original individidual layers and compiled it to make sure that areas that have multiple classifications under different legislation end up with the correct categories. 

Below is Robbie Economos' classification which I have loosely used:  
1. Nature Reserve  
2. National Park  
3. State Recreation Area  
4. Ramsar Wetlands  
5. State Forest Flora Reserves  
5. Conservation Agreements  
6. SEPP No. 14 and SEPP 26  
7. Wildlife Refuge  
 
* Protected area (Unknown)  
* Registered Property Agreements (Unknown)  
* Commonwealth heritage public  (Unknown) 


```{r setup, warning=FALSE,error=FALSE,echo=FALSE,message=FALSE,tidy=TRUE, results='hide'}
rm(list=ls())

packages(maptools)
packages(sp)
packages(rgeos)
packages(raster)

opts_chunk$set(dev="png", dev.args=list(type="cairo"), dpi=96, warning=FALSE,error=FALSE,echo=FALSE,message=FALSE,tidy=TRUE, results='hide')

setwd("~/GIS_data/Hunter/Plans/PA data for Amy - LH/")
output.directory <- "~/GIS_data/Hunter/Plans/PA data for Amy - LH/rasters/"

GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

create.raster <- function (s, mask.raster, raster.label, value=1, transform=FALSE) {
    
   if(transform==TRUE) {
     proj4string(s) <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
    s <- spTransform(s, CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
     }
    
  r <- rasterize(s,mask.raster)
    r[!is.na(r)] <- value
    r <- mask(merge(r,mask.raster),mask.raster, filename=paste0(output.directory,raster.label), format="GTiff", overwrite=T)
    names(r) <- rep(raster.label,length(names(r)))
    
    plot(r, main=raster.label,zlim=c(0,3),legend=F,axes=F)

    return(r)
  }

LH.mask <- raster("~/GIS_data/Hunter/mask files/LH.mask.tif")
  LH.mask[!is.na(LH.mask)] <- 0

 LH.clipping.mask <- raster("~/GIS_data/Hunter/mask files/LH.clipping.mask.tif")
 # set the background cells in the raster to 0
  LH.clipping.mask[!is.na(LH.clipping.mask)] <- 0

```

**Conservation Layers**  
Based on the following shapefiles:
* NPWSReserves.shp  
* ConservationAgreementsLowerHunter.shp  
* RegisteredPropertyAgreementsLowerHunter.shp  
* WildlifeRefugesLowerHunter.shp  
* CAPAD_ext_LH.shp  
* ramsar_wetlands_LH.shp  
* sepp14_shape.shp  
* SEPP26.shp  
 

```{r import conservation layers, warning=FALSE,error=FALSE,echo=FALSE,message=FALSE,tidy=TRUE, results='hide'}
setwd("~/GIS_data/Hunter/Plans/PA data for Amy - LH/")

# National parks
  NPWS.shp <- readShapePoly("Data layers for v1/NationalParks/NPWSReserves.shp", proj4 = GDA94)

  NPWS.raster <- create.raster(NPWS.shp[grepl(c("NP|NR|RP|SC"),NPWS.shp$reservetyp),],LH.mask,raster.label = "NPWS.reserves", transform=TRUE, value=3)


## Conservation Partners Data
  
# Conservation Agreements
  Conservation_agreements <- readShapePoly("Data layers for v1/Conservation Partners Data/ConservationAgreementsLowerHunter.shp", proj4string=GDA94)

  Cons.Agree.raster <- create.raster(Conservation_agreements,LH.mask,"ConservationAgreementsLowerHunter",transform=TRUE,value=3)

# Registered Property Agreements
  Reg.prop.agreements <- readShapePoly("Data layers for v1/Conservation Partners Data/RegisteredPropertyAgreementsLowerHunter.shp", proj4string=GDA94)

  Reg.prop.raster <- create.raster(Reg.prop.agreements,LH.mask,"RegisteredPropertyAgreementsLowerHunter",transform=TRUE,value=1)

# Wildlife refuges
  wildlife_refuges <- readShapePoly("Data layers for v1/Conservation Partners Data/WildlifeRefugesLowerHunter.shp", proj4string=GDA94)
  wildlife_refuges.raster <- create.raster(wildlife_refuges,LH.mask,"wildlifeRefugesLowerHunter",transform=TRUE,value=1)

# Protected Areas
  capad <- readShapePoly("Data layers for v1/ProtectedAreas/CAPAD_ext_LH.shp",proj4string=GDA94)

  capad_3.raster <- create.raster(capad[grepl(c("National Park|Nature Reserve|Aboriginal Area|State Conservation Area|Regional Park"),capad$TYPE),], LH.mask, "capad3",transform=TRUE,value=3)

  capad_2.raster <- create.raster(capad[grepl(c("Flora Reserve"),capad$TYPE),], LH.mask, "capad2",transform=TRUE,value=2)

  capad_1.raster <- create.raster(capad[grepl(c("Protected area"),capad$TYPE),], LH.mask, "capad1",transform=TRUE,value=1)

# Ramsar wetlands
  ramsar.shp <- readShapePoly("Data layers for v1/ramsar_wetlands_for_download/ramsar_wetlands_LH.shp", proj4string=GDA94)

  ramsar.raster <- create.raster(ramsar.shp,LH.mask,"ramsar",transform=TRUE,value=2)

# SEPP 14
  sepp14.shp <- readShapePoly("Data layers for v1/sepp14 coastal protection/sepp14_shape.shp", proj4string=GDA94)

  sepp14.raster <- create.raster(sepp14.shp,LH.mask,"SEPP14", transform=TRUE,value=2)

# SEPP 26
  sepp26.shp <- readShapePoly("Data layers for v1/sepp26 littoral rainforest/SEPP26.shp", proj4string=GDA94)

  sepp26.raster <- create.raster(sepp26.shp,LH.mask,"SEPP26", transform=TRUE,value=2)

```

**Heritage Layers**  
Based on three shapefiles:  
* commonwealth_heritage_public_LH.shp (after removing the Williamtown RAAF Base Group)  
* LH_Commonwealth_Lands.shp  
* WilliamtownRAAF_HeritageSites.shp  

```{r import heritage layers, warning=FALSE,error=FALSE,echo=FALSE,message=FALSE,tidy=TRUE, results='hide'}
setwd("~/GIS_data/Hunter/Plans/PA data for Amy - LH/")

# Heritage
  com_heritage <- readShapePoly("Data layers for v1/commonwealth_heritage_public/commonwealth_heritage_public_LH.shp", proj4string=GDA94.56)
    #remove the polygons associated with the airport
    com_heritage <- com_heritage[com_heritage$NAME!="Williamtown RAAF Base Group",]
  
  com_heritage_raster <- create.raster(com_heritage, LH.mask,raster.label="commonwealth_heritage_public",value=2)

# LH Commonwealth Lands (These seem like a strange thing to include - not really a protected area)
  commonwealth.lands <- readShapePoly("Additional data layers for v2/Commonwealth Lands/data/LH_Commonwealth_Lands.shp", proj4string=GDA94)

  commonwealth.lands.raster <- create.raster(commonwealth.lands, LH.mask, "CommonwealthLands",transform=TRUE,value=2)

# Williamtown Heritage Sites
  WHS <- readShapePoly("Additional data layers for v2/Heritage sites around WilliamtownRAAF/WilliamtownRAAF_HeritageSites.shp", proj4string=GDA94)

  WHS.raster <- create.raster(WHS,LH.mask, "WilliamtownRAAF_HeritageSites", transform=T, value=3)

```

The spatial data have been classified into three levels of security as defined below:

**High**  
* National Park  
* Nature Reserve  
* Ramsar  

**Medium**  
* State Conservation Area  
* Regional Park  
* Flora Reserve (Flora Management areas within State Forests)  
* Protected Area (Forest Management areas within State Forests)  
* Conservation Agreements  
* WilliamtownRAAF_HeritageSites  
* Commonwealth Lands (Largely defence housing and postoffices)  
* Commonwealth Heritage (excluding the Williamtown RAAF Base Group)  
* Aboriginal Area (based on CAPAD)  

**Low**  
* SEPP 14  
* SEPP 26  
* Registered property agreements  
* Wildlife Refuges  

These were then merged to create one layer representing the security of protected areas.  Where areas with differing classifications overlapped, the highest security level was assigned.

```{r merge rasters, warning=FALSE,error=FALSE,echo=FALSE,message=FALSE,tidy=TRUE, results='hide'}
setwd("~/GIS_data/Hunter/Plans/PA data for Amy - LH/")

protected.areas <- calc(stack(com_heritage_raster,NPWS.raster,Cons.Agree.raster,Reg.prop.raster,wildlife_refuges.raster,capad_1.raster,capad_2.raster,capad_3.raster,ramsar.raster,sepp14.raster,sepp26.raster,commonwealth.lands.raster,WHS.raster),max)

  protected.areas <- protected.areas + 3  
    writeRaster(protected.areas, filename=paste0(output.directory,"ProtectedAreas_v3"), format="GTiff", overwrite=T)

# create constant protected areas layer
  protected.areas.constant <- protected.areas
  protected.areas.constant[protected.areas.constant>3] <- 4
  writeRaster(protected.areas.constant, filename=paste0(output.directory,"ProtectedAreas_Constant_v3"), format="GTiff", overwrite=T)

  
plot(protected.areas, zlim=c(3,6),legend=F,col = rev(terrain.colors(4)), main="Security of Protected Areas",axes=F)
    legend("bottomright", bty="n",legend = c("High", "Medium", "Low"), fill = terrain.colors(4)[1:3])
plot(protected.areas.constant, legend=F,col = rev(terrain.colors(2)), main="Protected Areas",axes=F)

```

The security layer was then clipped by the Lower Hunter vegetation mask for inclusion in the Zonation analyses.

```{r clip protected areas by vegetation mask for zonation, warning=FALSE,error=FALSE,echo=FALSE,message=FALSE,tidy=TRUE, results='hide'}
setwd("~/GIS_data/Hunter/Plans/PA data for Amy - LH/")
  
protected.areas.constant.clip <- mask(protected.areas.constant,LH.clipping.mask, filename=paste0(output.directory,"ProtectedAreas_Constant_v3_clipped"), format="GTiff", overwrite=T)

protected.areas.clip <- mask(protected.areas,LH.clipping.mask, filename=paste0(output.directory,"ProtectedAreas_v3_clipped"), format="GTiff", overwrite=T)


plot(protected.areas.constant.clip, legend=F, main="Protected Areas (clipped)",axes=F)

plot(protected.areas.clip, zlim=c(3,6),legend=F,col = rev(terrain.colors(4)), main="Security of Protected Areas (clipped)",axes=F)
    legend("bottomright", bty="n",legend = c("High", "Medium", "Low"), fill = terrain.colors(4)[1:3])

```


```{r create word document, echo=FALSE,eval=FALSE}
setwd("~/RSP/R Code")
name <- "create and classify protected areas layer"
library(knitr)
library(pander)
knit(paste0(name, ".Rmd"), encoding = "utf-8")
name <- "create and classify protected areas layer"
Pandoc.brew(file = paste0(name, ".md"), output = name, convert = "docx")

```

***
*This file was last updated on 04 March 2014 and last run on `r format(Sys.time(), "%d %B %Y")`.*