Create extant vegetation layer to clip all layers for zonation
========================================================

Create a clippling mask that is used to cut the MaxEnt output for use in Zonation.  Currently only includes remnant vegetation 
* final vegetation (GH)

* Probably need to add a solid GH layer as well 

```{r setup_functions}
#load library and set working directory
  rm(list=ls())
  
  library(raster)
  library(rgdal)
  library(maptools)
  library(rgeos)
  source("R code/shp2raster.R")

#   computer <- "//654cw-20990/Amy"
#   computer <- "I:/Super Computer Data"
  computer <- "H:/UM backup"
#   computer <- "Z:/Amy"

  GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

# Lakes
  lakes <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/Lakes/Lakes.shp"),proj4string=CRS("+proj=utm +zone=56 +south +ellps=aust_SA +units=m +no_defs"))
    lakes <- spTransform(lakes,GDA94.56)

# GH & PM boundary
  GH_PM.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/GH_PM.mask.tif"))

# GH administrative boundary
#   GH.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/GH.mask.tif"))

# GH shapefile
  GH.shp <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From HCCREMS/Boundaries/AoI/HCCREMS_LGA.shp"),proj4=GDA94)
    GH.shp <- spTransform(GH.shp,GDA94.56)
  HV.shp <- GH.shp[grepl("NEWCASTLE|PORT STEPHENS|MAITLAND|CESSNOCK|LAKE MACQUARIE|WYONG|GOSFORD",GH.shp$lganame),]
#     HV.shp <- spTransform(HV.shp,GDA94.56)

  GH.mask <- mask(crop(GH_PM.mask,GH.shp),GH.shp,filename=paste0(computer,"/GIS_data/Hunter/mask files/GH.mask.tif"),overwrite=T)
  
# LH administrative boundary
  LH.shp <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/OEH_Lower_Hunter_18122012/Administrative/5_LGAs_StudyArea.shp"), proj4=GDA94.56)

  
# create LH mask, snapping to the GH mask
  LH.mask <- crop(rasterize(LH.shp,GH_PM.mask,value=1),LH.shp, filename=paste0(computer,"/GIS_data/Hunter/mask files/LH.mask.tif"),overwrite=T)

# UH administrative boundary bounded by HCCREMS AoI
  UH.shp <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/Upper Hunter Strategic Assessment Review/AoI/UHSA_StudyArea_within_HCCREMS.shp"),proj4=GDA94)
    UH.shp <- spTransform(UH.shp,GDA94.56)
  
# create LH mask, snapping to the GH mask
  UH.mask <- crop(rasterize(UH.shp,GH_PM.mask,value=1),UH.shp, filename=paste0(computer,"/GIS_data/Hunter/mask files/UH_HCCREMS.mask.tif"),overwrite=T)

# create Hunter Valley (7 LGA) mask
  HV.mask <- crop(rasterize(HV.shp,GH_PM.mask,value=1),HV.shp, filename=paste0(computer,"/GIS_data/Hunter/mask files/HV.mask.tif"),format="GTiff",overwrite=T)

# create Port Macquarie mask
 PM.shp <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/Port MacQuarie/PMHC LGA boundary.shp"))
    PM.mask <- crop(rasterize(PM.shp,GH_PM.mask,value=1),PM.shp, filename=paste0(computer,"/GIS_data/Hunter/mask files/PM.mask.tif"),format="GTiff",overwrite=T)
```

The clipping masks are based on remnant vegetation after standardising the layer for all other data layers included in the Maxent models.  This removes areas where data may be missing in any layer.  
* Note that this means the `standardise raster files for spatial analyses_mark2.Rmd` may need to be run again before creating the clipping layers if any of the environmental layers change

```{r create clipping masks}
# LH_LZN_Existing_Urban_Areas_OEH_Revised
  LH.existing.urban <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From OEH/Raw data for RGP report/LH_LZN_Existing_Urban_Areas_OEH_Revised.shp"))

  LH.exurban.mask <- shp2raster(LH.existing.urban,LH.mask,value=0,bkg=1,label="LH.urban.mask",save=F)
    LH.exurban.mask[LH.exurban.mask==0] <- NA

# remove lakes from the urban layer
    LH.lakes.mask <- shp2raster(lakes,LH.mask,value=0,bkg=1,label="lakes",save=F)
    LH.lakes.mask[LH.lakes.mask==0]<-NA

writeRaster(LH.lakes.mask,paste0(computer,"/GIS_data/Hunter/mask files/LH.lakes.mask.tif"),overwrite=T)

LH.exurban.mask <- min(LH.exurban.mask,LH.lakes.mask)

  writeRaster(LH.exurban.mask,paste0(computer,"/GIS_data/Hunter/mask files/LH.urban.clipping.mask.tif"),overwrite=T)

# Greater Hunter & Port Mac clipping mask
  GH_PM.veg <- raster(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/environmental_data/standardised_rasters/final_vegetation.asc"),crs=GDA94.56)
  GH_PM.veg[GH_PM.veg==0] <- NA  
  GH_PM.veg[!is.na(GH_PM.veg)] <- 1
  writeRaster(GH_PM.veg,filename=paste0(computer,"/GIS_data/Hunter/mask files/GH_PM.clipping.mask.tif"),overwrite=T)

# Greater Hunter clipping mask
  GH.veg <- mask(crop(GH_PM.veg,GH.mask),GH.mask)
  writeRaster(GH.veg,filename=paste0(computer,"/GIS_data/Hunter/mask files/GH.clipping.mask.tif"),overwrite=T)

# LH clipping mask
  LH.veg <- mask(crop(GH_PM.veg,LH.mask),LH.exurban.mask,filename=paste0(computer,"/GIS_data/Hunter/mask files/LH.clipping.mask.tif"),overwrite=T)

# UH clipping mask
UH.veg <- mask(crop(GH_PM.veg,UH.mask),UH.mask,filename=paste0(computer,"/GIS_data/Hunter/mask files/UH_HCCREMS.clipping.mask.tif"),overwrite=T)

# HV clipping mask
HV.veg <- mask(crop(GH_PM.veg,HV.mask),HV.mask,filename=paste0(computer,"/GIS_data/Hunter/mask files/HV.clipping.mask.tif"),overwrite=T)

# PM clipping mask
PM.veg <- mask(crop(GH_PM.veg,PM.mask),PM.mask,filename=paste0(computer,"/GIS_data/Hunter/mask files/PM.clipping.mask.tif"),overwrite=T)

```

```{r wyong}
# wyong clipping mask
wyong.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/wyong.mask.tif"))
wyong.veg <- readShapePoly(paste0(computer,"/GIS_data/Hunter/vegetation/Vegetation2008_WSC_20140716.shp"),proj4string=GDA94.56)

# Force Tuggerah Lakes EEC into clipping mask
tuggerah.lakes <- readShapePoly(paste0(computer,"/GIS_data/Wyong/Wyong Shire Council Data/Species/TuggerahLakesSaltmarsh(EEC)_WSC_20140716.shp"),proj4string=GDA94.56)
tuggerah.lakes.dist <- readShapePoly(paste0(computer,"/GIS_data/Wyong/Wyong Shire Council Data/Species/TuggerahLakesSaltmarshDisturbedZone(EEC)_WSC_20140716.shp"),proj4string=GDA94.56)

tuggerah.lakes.mask <- shp2raster(gBuffer(tuggerah.lakes,width=100),wyong.mask,value=1,bkg=0,label="TuggerahLakesSaltmarsh(EEC)_WSC_20140716",save=F)
tuggerah.lakes.dist.mask <- shp2raster(gBuffer(tuggerah.lakes.dist,width=100),wyong.mask,value=0.5,bkg=0,label="TuggerahLakesSaltmarshDisturbedZone(EEC)_WSC_20140716",save=F)

tuggerah.lakes.combined <- sum(tuggerah.lakes.mask,tuggerah.lakes.dist.mask)
  tuggerah.lakes.combined[tuggerah.lakes.combined>0] <- 1
  tuggerah.lakes.combined[tuggerah.lakes.combined==0] <- NA

# Tetratheca juncea
  tet.jun <- readShapePoints(paste0(computer,"/GIS_data/Wyong/Wyong Shire Council Data/Species/Tetratheca_juncea_WSC_20140716.shp"),proj4string=GDA94.56)
  
  tet.jun.mask <- shp2raster(gBuffer(tet.jun,width=100),wyong.mask,value=1,bkg=NA,label="Tetratheca_juncea_WSC_20140716",save=F)

# Corunastylis_charmhaven
  cor.cha <- readShapePoly(paste0(computer,"/GIS_data/Wyong/Wyong Shire Council Data/Species/Corunastylis_charmhaven_WSC_20140804.shp"),proj4string=GDA94.56)
  cor.cha.mask <- shp2raster(gBuffer(cor.cha,width=50),wyong.mask,value=1,bkg=NA,label="Corunastylis_charmhaven_WSC_20140804",save=F)

# Corunastylis_insignis
  cor.ins <- readShapePoly(paste0(computer,"/GIS_data/Wyong/Wyong Shire Council Data/Species/Corunastylis_insignis_WSC_20140804.shp"),proj4string=GDA94.56)
  cor.ins.mask <- shp2raster(gBuffer(cor.ins,width=50),wyong.mask,value=1,bkg=NA,label="Corunastylis_insignis_WSC_20140804",save=F)

# Thelymitra adorata
  the.ado <- readShapePoly(paste0(computer,"/GIS_data/Wyong/Wyong Shire Council Data/Species/Thelymitra_adorata_WSC_20140804.shp"),proj4string=GDA94.56)
  the.ado.mask <- shp2raster(gBuffer(the.ado,width=50),wyong.mask,value=1,bkg=NA,label="Thelymitra_adorata_WSC_20140804",save=F)

# wyong mask with lakes removed
  wyong.lakes.mask <- shp2raster(lakes,wyong.mask,value=0,bkg=1,label="lakes",save=F)
    wyong.lakes.mask[wyong.lakes.mask==0]<-NA
  writeRaster(wyong.lakes.mask,filename=paste0(computer,"/GIS_data/Hunter/mask files/wyong.lakes.mask.tif"),format="GTiff",overwrite=T)

# create clipping mask based on vegetation
  wyong.veg.mask <- shp2raster(wyong.veg[!grepl("Plantation|Rock",wyong.veg$WYONG_VEG),],wyong.mask,label="WyongVeg2008",value=1,bkg=0,save = F)
  
# remove lakes
  wyong.clipping.mask <- mask(wyong.veg.mask,wyong.lakes.mask)

# add back in special feature areas
  wyong.clipping.mask <- merge(tuggerah.lakes.combined,tet.jun.mask,cor.cha.mask,the.ado.mask,wyong.clipping.mask)

  wyong.clipping.mask[wyong.clipping.mask>0] <- 1
  wyong.clipping.mask[wyong.clipping.mask==0] <- NA
writeRaster(wyong.clipping.mask,filename=paste0(computer,"/GIS_data/Hunter/mask files/wyong.clipping.mask.tif"),format="GTiff",overwrite=T)



```


*This file was last updated on 23 July 2014 and last run on `r format(Sys.time(), "%d %B %Y")`.*