Create extant vegetation layer to clip all layers for zonation
========================================================

Create a clippling mask that is used to cut the MaxEnt output for use in Zonation.  Currently only includes remnant vegetation 
* final vegetation (GH)

* Probably need to add a solid GH layer as well 

```{r setup_functions}
#load packages and set working directory
  rm(list=ls())
  
  packages(raster)
  packages(rgdal)
  packages(maptools)
  
  GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

# GH administrative boundary
  GH.mask <- raster("~/GIS_data/Hunter/mask files/GH.mask.tif")

# GH & PM boundary
  GH_PM.mask <- raster("~/GIS_data/Hunter/mask files/GH_PM.mask.tif")
  
# LH administrative boundary
  LH.shp <- readShapePoly("~/GIS_data/Hunter/All data from harddrive/From DO/OEH_Lower_Hunter_18122012/Administrative/LHRS_Study_Area.shp", proj4=GDA94.56)

  
# create LH mask, snapping to the GH mask
  LH.mask <- crop(rasterize(LH.shp,GH.mask),LH.shp, filename="~/GIS_data/Hunter/mask files/LH.mask.tif",format="GTiff",overwrite=T)

# UH administrative boundary bounded by HCCREMS AoI
  UH.shp <- readShapePoly("~/GIS_data/Hunter/All data from harddrive/Upper Hunter Strategic Assessment Review/AoI/UHSA_StudyArea_within_HCCREMS.shp",proj4=GDA94)
    UH.shp <- spTransform(UH.shp,GDA94.56)
  
# create LH mask, snapping to the GH mask
  UH.mask <- crop(rasterize(UH.shp,GH.mask,value=1),UH.shp, filename="~/GIS_data/Hunter/mask files/UH_HCCREMS.mask.tif",format="GTiff",overwrite=T)

```

The clipping masks are based on remnant vegetation after standardising the layer for all other data layers included in the Maxent models.  This removes areas where data may be missing in any layer.  
* Note that this means the `standardise raster files for spatial analyses_mark2.Rmd` may need to be run again before creating the clipping layers if any of the environmental layers change

```{r create clipping masks}
# LH_LZN_Existing_Urban_Areas_OEH_Revised
  LH.existing.urban <- readShapePoly("~/GIS_data/Hunter/All data from harddrive/From OEH/Raw data for RGP report/LH_LZN_Existing_Urban_Areas_OEH_Revised.shp")
  LH.exurban.mask <- mask(rasterize(LH.existing.urban,LH.mask,field=0,background=1),LH.mask)
    LH.exurban.mask[LH.exurban.mask==0] <- NA


# Greater Hunter clipping mask
  GH.veg <- raster("~/GIS_data/Hunter/Maxent_files/ghm_environmental_data/standardised_rasters/final_vegetation.asc",crs=GDA94.56)
    GH.veg[!is.na(GH.veg)] <- 1
  writeRaster(GH.veg,filename="~/GIS_data/Hunter/mask files/GH.clipping.mask.tif",format="GTiff",overwrite=T)

# Greater Hunter & Port Mac clipping mask
  GH_PM.veg <- raster("~/GIS_data/Hunter/Maxent_files/ghm.pm_environmental_data/standardised_rasters/final_vegetation.asc",crs=GDA94.56)
  GH_PM.veg[GH_PM.veg==0] <- NA  
  GH_PM.veg[!is.na(GH_PM.veg)] <- 1
  writeRaster(GH_PM.veg,filename="~/GIS_data/Hunter/mask files/GH_PM.clipping.mask.tif",format="GTiff",overwrite=T)

# LH clipping mask
  LH.veg <- mask(crop(GH.veg,LH.mask),LH.exurban.mask,filename="~/GIS_data/Hunter/mask files/LH.clipping.mask.tif",format="GTiff",overwrite=T)

# UH clipping mask
UH.veg <- mask(crop(GH.veg,UH.mask),UH.mask,filename="~/GIS_data/Hunter/mask files/UH_HCCREMS.clipping.mask.tif",format="GTiff",overwrite=T)

```


*This file was last updated on 11 March 2014 and last run on `r format(Sys.time(), "%d %B %Y")`.*