Extract records from Australia Living Atlas data
========================================================
This script extracts records of threatened species (& other species we are interested in) from the regional data files downloaded from the Australian Living Atlas and the NSW Atlas. 

Data were downloaded by selecting the NSW North Coast and Sydney Basin bioregions and then downloading all records within these region in large taxonomic blocks.  
 
The script uses a function `extract` to identify whether data for each species in `species.list` has been downloaded from the regional ALA database based on the scientific name.  Note that sub-species will be lumped together unless they are specifically listed in `species.list`. If data exists, the records for each species are saved as a separate csv file by their scientific name.  Data are not filtered by data or location quality at this stage. The master threatened species file is updated to reflect that the data has been downloaded and lists the number of records for that species from each database.  

The script loops through each taxonomic group and extracts the records for species listed in `threatened species` within each region.  It then combines the regional data together for each species.  A print out to the screen lists the number of records successfully downloaded for each available species and this data is also updated in the threatened species list.


```{r functions, highlight=TRUE}
# set working directory
rm(list=ls())
setwd("C:/Users/awhitehead/Documents/GIS_data/Hunter/species point data")

# a function that binds two dataframes together by rows, keeping only columns with the same names
rbind.match.columns <- function (input1,input2) {
    n.input1 <- ncol(input1)
    n.input2 <- ncol(input2)
    
    if(n.input2 < n.input1) {
      TF.names <- which(names(input2) %in% names(input1))
      column.names <- names(input2[,TF.names])
      } else {
        TF.names <- which(names(input1) %in% names(input2))
        column.names <- names(input1[,TF.names])
      }
    
    return(rbind(input1[,column.names], input2[,column.names]))
  }

# a function that extracts records for individual species based on the given region
extract <- function(folder, region, input,species){
  records <- input[grep(species,input$Scientific.Name),]
  if(nrow(records)>0) {
    cat(nrow(records), "records for",as.character(species),"successfully extracted from",region,"in",folder,"\n")
    return(records)
  } 
}

# a function that combines records from each region, allowing for the fact that they may be absent from a region
combine.records <- function (NC.records, SB.records) {
  tryCatch({
            rbind.match.columns(NC.records,SB.records)
            }, error = function(err){
              if(is.null(NC.records)==TRUE & is.null(SB.records)==FALSE){
                return(SB.records)
              } else if(is.null(SB.records)==TRUE & is.null(NC.records)==FALSE){
                return(NC.records)
              } else cat("")
            })
  }

#open mnes species list
# mnes.species <- read.csv("EPBC list species NSW.csv", skip=1)

mnes.species <- read.csv("C:/Users/awhitehead/Documents/GIS_data/Australia-wide/species data/all EPBC listed species 27May2013.csv")

# open the list of threatened and interesting species for potential analysis
protected.species <- read.csv("IBRA threatened species list.csv")
   protected.species$mnes <- "FALSE"
  protected.species$mnes[which(protected.species$Scientific.Name %in% mnes.species$scientific.name ==TRUE)] <- "TRUE"


# generate threatened species list
# threatened.species <- rbind(protected.species[grep("E", protected.species$NSW.status),], protected.species[grep("V", protected.species$NSW.status),], protected.species[grep("TRUE", protected.species$mnes),])
#   threatened.species <- threatened.species[!duplicated(threatened.species),]

threatened.species <- protected.species
 
# the taxanomic blocks that the data were downloaded in
taxa <- c("mammals", "amphibians", "plants", "reptiles","birds","arthropods")
          
```

```{r analysis_ALA}
setwd("C:/Users/awhitehead/Documents/GIS_data/Hunter/species point data")

# loop through each taxonomic group and extract records based on the threatened species list
for (k in seq(taxa)){
  cat("\n", "Extracting records for",taxa[k],"\n")  
  species.list <- threatened.species$Scientific.Name[threatened.species$Taxa==taxa[k]] 
  NC.input <- read.csv(paste0("ALA downloads/NSW North Coast ",taxa[k],".csv"))
  SB.input <- read.csv(paste0("ALA downloads/Sydney Basin ",taxa[k],".csv"))
  BB.input <- read.csv(paste0("ALA downloads/Brigalow Belt South ",taxa[k],".csv"))

  for(i in seq(species.list)){
      NC.records <- extract("ALA downloads", "NSW North Coast",NC.input,species.list[i])
      SB.records <- extract("ALA downloads", "Sydney Basin",SB.input,species.list[i])
      BB.records <- extract("ALA downloads", "Brigalow Belt South",BB.input,species.list[i])
      
      all.records <- combine.records(NC.records, SB.records)
        all.records <- combine.records(all.records, BB.records)
        
     if(is.null(all.records)==FALSE) {
        protected.species$Downloaded.ALA[protected.species$Scientific.Name==species.list[i]] <- "yes"
        protected.species$ALA.records[protected.species$Scientific.Name==species.list[i]] <- nrow(all.records)
        write.csv(all.records, glue("ALA data/",species.list[i],".csv"),row.names=FALSE)
        cat("Exported",nrow(all.records), "records for", as.character(species.list[i]),"\n","\n")
        }
      suppressWarnings(rm(NC.records,SB.records,BB.records,all.records))
      gc()
    }
}

# update threatened species download information
write.csv(protected.species, "IBRA threatened species list.csv", row.names=FALSE)

```


```{r analysis_NSW}
setwd("C:/Users/awhitehead/Documents/GIS_data/Hunter/species point data")

# loop through each taxonomic group and extract records based on the threatened species list
for (k in seq(taxa)){
  cat("\n", "Extracting records for",taxa[k],"\n")  
  species.list <- threatened.species$Scientific.Name[threatened.species$Taxa==taxa[k]] 
   NC.input <- read.csv(paste0("NSW Atlas downloads/NSW North Coast ",taxa[k],".csv"))
    colnames(NC.input)[8] <- "Scientific.Name"
  SB.input <- read.csv(paste0("NSW Atlas downloads/Sydney Basin ",taxa[k],".csv"))
    colnames(SB.input)[8] <- "Scientific.Name"
  BB.input <- read.csv(paste0("NSW Atlas downloads/Liverpool Range ",taxa[k],".csv"))
    colnames(BB.input)[8] <- "Scientific.Name"
  for(i in seq(species.list)){
      NC.records <- extract("NSW Atlas downloads", "NSW North Coast",NC.input,species.list[i])
      SB.records <- extract("NSW Atlas downloads", "Sydney Basin",SB.input,species.list[i])
      BB.records <- extract("NSW Atlas downloads", "Liverpool Range",BB.input,species.list[i])
      
      all.records <- combine.records(NC.records, SB.records)
        all.records <- combine.records(all.records, BB.records)
      
      coordinates(all.records) <- c("Longitude_GDA94","Latitude_GDA94")
      projection(all.records) <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
      all.records <- spTransform(all.records,CRS("+proj=lcc +lat_1=-18 +lat_2=-36 +lat_0=0 +lon_0=134 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
        
     if(is.null(all.records)==FALSE) {
        protected.species$Downloaded.NSW[protected.species$Scientific.Name==species.list[i]] <- "yes"
        protected.species$NSW.records[protected.species$Scientific.Name==species.list[i]] <- nrow(all.records)
        write.csv(all.records, glue("NSW Atlas data/",species.list[i],".csv"),row.names=FALSE)
        cat("Exported",nrow(all.records), "records for", as.character(species.list[i]),"\n","\n")
        }
      suppressWarnings(rm(NC.records,SB.records,BB.records,all.records))
      gc()
    }
}

# update threatened species download information
write.csv(protected.species, "IBRA threatened species list.csv", row.names=FALSE)

```


```{r analysis_OEH}
setwd("C:/Users/awhitehead/Documents/GIS_data/Hunter/species point data")

# loop through each taxonomic group and extract records based on the threatened species list

  cat("\n", "Extracting records for OEH","\n")  
  species.list <- threatened.species$Scientific.Name 
   OEH.input <- read.csv(paste0("OEH/OEH_UH_species_data.csv"))
    # remove records with missing spatial data  
    OEH.input <- OEH.input[!is.na(OEH.input$easting),]

# convert OEH to WGS84 to match rest of data
  coordinates(OEH.input) <- c("easting", "northing")
    
    # set current projection
    proj4string(OEH.input) <- "+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs" 
  
    # transform to new projection
    project_OEH.input <- spTransform(OEH.input, CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
  
    # convert back to a dataframe
    OEH.input <- as.data.frame(project_OEH.input)
      names(OEH.input)[21:22] <- c("longitude","latitude")

   
  for(i in seq(species.list)){
      OEH.records <- extract("OEH", "OEH",OEH.input,species.list[i])
              
     if(is.null(OEH.records)==FALSE) {
        protected.species$Downloaded.OEH[protected.species$Scientific.Name==species.list[i]] <- "yes"
        protected.species$OEH.records[protected.species$Scientific.Name==species.list[i]] <- nrow(OEH.records)
        write.csv(OEH.records, glue("OEH data/",species.list[i],".csv"),row.names=FALSE)
        cat("Exported",nrow(OEH.records), "records for", as.character(species.list[i]),"\n","\n")
        }
      suppressWarnings(rm(OEH.records,all.records))
      gc()
    }

# update threatened species download information
write.csv(protected.species, "IBRA threatened species list.csv", row.names=FALSE)

```
*This file was last updated on 12 April 2013 and last run on `r format(Sys.time(), "%d %B %Y")`.*