Identify species in Lower Hunter with low AUC values
========================================================

This script should identify those species within the lower hunter that have an AUC value below a given threshold and generate a raster file based on the point data.

Set the threshold with auc.threshold.


```{r setup}
rm(list=ls())

library(raster)

computer <- "~" #My computer
#computer <- "Z:/Amy" #Super computer

input.dir <- paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/")

output.dir <- paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/tifs for species with low auc values/")
  
taxa <- c("amphibians","birds","mammals","plants","reptiles")

auc.threshold <- 0.5

 hunter.mask <- raster(paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/output_lower.hunter_all.rank.asc"))
  
  mask.raster <- raster(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm_environmental_data/standardised_rasters/final_vegetation.asc"))
   # set the background cells in the raster to 0
    mask.raster[!is.na(mask.raster)] <- 0
    mask.raster <- mask(crop(mask.raster,hunter.mask),hunter.mask)

point.data <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/species_data/maxent.data_ALA.NSW.csv"))
  

```

```{r presence absence raster function}

presence.absence.raster <- function (mask.raster,species.data,raster.label="") {
      #set the cells that contain points to 1
    speciesRaster <- rasterize(species.data,mask.raster,field=1)
      speciesRaster <- mask(merge(speciesRaster,mask.raster),mask.raster)
      #label the raster
      names(speciesRaster) <- raster.label
    #plot(speciesRaster,main=raster.label)
      writeRaster(speciesRaster,paste0(output.dir,raster.label,"_LH.tif"), format="GTiff",overwrite=T)
    cat("Converted",raster.label,"to raster","\n")
    gc()
  }

```

This chunk loops through the five taxa and identifies which species have auc values below the threshold after they have been cut to the Lower Hunter.  It prints a table of the species and their auc value before extracting the points from the original MaxEnt data.  These points are then converted them to a presence absence raster for the Lower Hunter and are saved in the output directory specified by out.dir


```{r identify species}

for(t in seq(taxa)){
  cat("\n", "Checking",taxa[t], "for species below the threshold","\n")
  auc.values <- read.csv(paste0(computer,"/GIS_data/Hunter/zonation/sdm_max_values_",taxa[t],".csv"))
    colnames(auc.values) <- c("species", "GH.auc", "LH.auc")
  
  print(species.of.interest <- auc.values[auc.values$max.tif < auc.threshold,])
  
  species.list <- species.of.interest$species
    if(length(species.list)>0){
      species.list <- gsub("_avg.asc","",species.list)
      species.list <- gsub("_"," ",species.list)
     
    for(i in seq(species.list)){
      species.data <- point.data[point.data$species == species.list[i],]
      species.data <- species.data[,2:3]
      species.list[i] <- gsub(" ","_",species.list[i])
      presence.absence.raster(mask.raster,species.data, raster.label=species.list[i])
      
      }
    rm(species.list)  
    }
  }



```

