Merge Port MacQuarie polygon into GH clipping mask
========================================================

Merge the Port MacQuarie polygon into the existing greater hunter mask and export as a new mask raster file

```{r}
rm(list=ls())
packages(raster)
packages(rgdal)
source("C:/Users/awhitehead/Dropbox/Random R code/shp2raster.R")

# projections 
  GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")


port.mac.dir <- "~/GIS_data/Hunter/All data from harddrive/Port MacQuarie/"
setwd(port.mac.dir)

port.mac <- readOGR(dsn=".",layer="PMHC LGA boundary")

gh.raster <- raster("~/GIS_data/Hunter/mask files/GH.mask.tif")
  writeRaster(gh.raster, "~/GIS_data/Hunter/mask files/GH.mask_old.tif")
  gh.raster <- extend(gh.raster,c(197142,497753.4,6282948,6557576))
  gh.raster[!is.na(gh.raster)] <- 1
  gh.raster[is.na(gh.raster)] <- 0

  GH_PM <- shp2raster(port.mac,gh.raster,value=1,bkg=0,label="GH_PM",save=F,mask=F)
    GH_PM <- sum(gh.raster,GH_PM)
    GH_PM[GH_PM==0] <- NA
    GH_PM[!is.na(GH_PM)] <- 0
  writeRaster(GH_PM,"~/GIS_data/Hunter/mask files/GH.mask.tif",format="GTiff",overwrite=T)

```

```{r create individal council raster masks}

 port.mac.raster <- mask(crop(GH_PM,port.mac),port.mac,"~/GIS_data/Hunter/mask files/PortMac.mask.tif",format="GTiff",overwrite=T)

  wyong.dir <- "~/GIS_data/Hunter/All data from harddrive/Wyong/"
  setwd(wyong.dir)
  
  wyong <- readOGR(dsn=".",layer="Wyong_boundary")
    wyong <- spTransform(wyong,GDA94.56)

  wyong.mask <- crop(mask(shp2raster(wyong,gh.raster,value=0,bkg=0,label="wyong.mask",save=F,map=F),wyong),wyong,"~/GIS_data/Hunter/mask files/wyong.mask.tif",format="GTiff",overwrite=T)

