Reclassify the PB vegetation data and combine with Upper Hunter

```{r setup}
rm(list=ls())
start.time <- proc.time()

  envi.directory <- "~/GIS_data/Hunter/vegetation/"
  output.directory <- "~/GIS_data/Hunter/vegetation/"

setwd(output.directory)

packages(raster)
packages(rgdal)
packages(maptools)

greater.hunter <- raster("~/GIS_data/Hunter/Maxent_files/ghm_environmental_data/hccrems_mask.asc")
lower.hunter <- raster("~/GIS_data/Hunter/zonation/lower hunter/output_lower.hunter_all.rank.asc")


ghm.veg <- raster("GHM raster data/vegetation")
ghm.veg.reclass <- read.csv("ghm_veg_reclassify.csv")
for(i in seq(ghm.veg.reclass$GHM_num)){
     ghm.veg[ghm.veg==ghm.veg.reclass$GHM_num[i]] <- ghm.veg.reclass$Mosiac_num[i]+100 
}

ghm.veg <- ghm.veg - 100

lh.veg <- raster("LH_Kform")
lh.veg.reclass <- read.csv("lh_veg_reclassify.csv")
for(i in seq(lh.veg.reclass$PB_num)){
     lh.veg[lh.veg==lh.veg.reclass$PB_num[i]] <- lh.veg.reclass$Mosiac_num[i]+100 
}

lh.veg <- lh.veg - 100

lh.veg.resamp <- resample(lh.veg,ghm.veg)

final.veg <- merge(lh.veg.resamp,ghm.veg,filename="~/GIS_data/Hunter/Maxent_files/ghm_environmental_data/vegetation/final_vegetation.tif",ovewrite=T)


# Don't do it - it will take forever and then die!
#ghm.veg <- readShapePoly("GHMv4_veg.shp")

veg_reclasses <- read.csv("reclassifying_hunter_veg.csv")

create.raster <- function (s, mask.raster, label, field, transform=TRUE) {
    
   if(transform==TRUE) {
     proj4string(s) <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
    s <- spTransform(s, CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
     }
    
  r <- rasterize(s,mask.raster, field)
    r <- mask(merge(r,mask.raster),mask.raster)
    names(r) <- label
    
    plot(r, main=label)
    
   writeRaster(r,paste0(output.directory,label), format="GTiff", overwrite=T)
    return(r)
  }

```

Not sure we actually to do this step anymore

```{r reclassify}
lh.mosiac <- veg_reclasses[1:13,c(3,4)]

new_lh <- reclassify(lh.veg, d(is=lh.mosiac[,1],becomes=lh.mosiac[,2]))

```


```{r reclassify K formation}

# veg types to reclassify
veg.classes <- unique(lh.veg$VegCommNam[is.na(lh.veg$Formation_)])

# add new levels to field
levels(lh.veg$Amy_Kforma) <- c(levels(lh.veg$Amy_Kforma),"Water", "Exotic", "Naturally bare", "Disturbed", "Other", "Dry Sclerophyll", "Wet Sclerophyll")

# Water
water <- veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Water"]
 lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% water==TRUE)] <- "Water"

# Exotic
exotic <- veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Exotic"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% exotic==TRUE)] <- "Exotic"

#Naturally bare ground
bare.ground <-  veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Naturally bare"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% bare.ground==TRUE)] <- "Naturally bare"
  
# Disturbed vegetation
disturbed <-  veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Disturbed"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% disturbed==TRUE)] <- "Disturbed"

# Dry Sclerophyll
lh.veg$Amy_Kforma[grep("Dry Sclerophyll", lh.veg$Amy_Kforma)] <- "Dry Sclerophyll"
 dry.sclerophyll <- veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Dry Sclerophyll"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% dry.sclerophyll==TRUE)] <- "Dry Sclerophyll"

# Wet Scelrophyll
lh.veg$Amy_Kforma[grep("Wet Sclerophyll", lh.veg$Amy_Kforma)] <- "Wet Sclerophyll"
wet.sclerophyll <- veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Wet Sclerophyll"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% wet.sclerophyll==TRUE)] <- "Wet Sclerophyll"
  
# other
other <- veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Other"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% other==TRUE)] <- "Other"

#Grassy Woodlands
grassy.woodlands <- veg_reclasses$VegCommNam[veg_reclasses$VegCommNam_reclass == "Grassy Woodlands"]
  lh.veg$Amy_Kforma[which(lh.veg$VegCommNam %in% grassy.woodlands==TRUE)] <- "Grassy Woodlands"

unique(lh.veg$VegCommNam[is.na(lh.veg$Amy_Kforma)])
veg_reclasses$final_Kforma <- unique(lh.veg$Amy_Kforma)
veg_reclasses$final_Kforma_num <- as.numeric(as.factor(veg_reclasses$final_Kforma))

# write.csv(veg_reclasses, "PB_veg.classes.csv")

```

What are we doing with the bits that haven't been reclassified?  How do we want to define non-native vegetation, recognising that it won't all necessarily be the same.

```{r rasterise PB_vegetation}

lh.veg.raster <- create.raster(lh.veg[!is.na(lh.veg$Amy_Kforma),], greater.hunter, field="Amy_Kforma", transform=FALSE, label="LH_veg")

rasterize(lh.veg,greater.hunter,field="VegID", update=T)

Amy_Kforma_num <- as.numeric(as.factor(lh.veg$Amy_Kforma))

test <- rasterize(lh.veg,greater.hunter,update=T,field=Amy_Kforma_num)
```

Can we just overwrite the GHM values in the lower hunter with the reclassified data?  Need to check that the values will be the equivalent. 

If that's it, then we just need to generate the % cover values and then we can rerun the SDMs.

```{r reclassify GHM }

lh.veg.raster <- create.raster(lh.veg[!is.na(lh.veg$Amy_Kforma),], greater.hunter, field="Amy_Kforma", transform=FALSE, label="LH_veg")

lh.veg.raster <-rasterize(lh.veg,greater.hunter,field="VegID", update=T)

Amy_Kforma_num <- as.numeric(as.factor(lh.veg$Amy_Kforma))

test <- rasterize(lh.veg,greater.hunter,update=T,field=Amy_Kforma_num)
```