Identify species with points in LHSA
========================================================

# Species
1. Check for Maxent species that have points within the Lower Hunter
2. Clip the extant distribution for species with at least 1 point in the LH
3. Compare the clipped LH species distributions with the GH distribution and replace species where the LH.max or AUC value is below the thresholda with a presence-absence raster
4. Create Presence-absence rasters for all point species

# TECs
5. Check TECS that have points in the LH
6. Clip the extant distribution of TECS with at least 1 point in the LH
7. Compare the clipped LH TEC distributions with the GH distribution and replace species where the LH.max is below the threshold with a presence-absence raster
8. Create Presence-absence rasters for all point tecs

9. Clip all pre1750 SDMs to LH based on the extant LH SDMs that have been retained.

10. Check that all layers are the same dimensions

11. Create spp files


```{r}
rm(list=ls())

library(raster)


#computer <- "~" #My computer
computer <- "Z:/Amy" #Super computer
# computer <- "//654cw-20990/Amy"

# clip pre1750 layers?
  pre1750 <- TRUE
  clip <- FALSE

# directories
  maxent.dir <- paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/all_variables/output/")
# location of GH files
  GH_PM.zonation.dir <- paste0(computer,"/GIS_data/Hunter/zonation/GH_PM/")

# location of LH files
  LH.zonation.dir <- paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/") 

# set projections
  GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

# import region mask for LHSA
 LH.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/LH.mask.tif"))
  LH.mask[!is.na(LH.mask)] <- 0

# LHSA clipping mask
  LH.clipping.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/LH.clipping.mask_v2.tif"))
    LH.clipping.mask[!is.na(LH.clipping.mask)] <- 0

# LHSA urban clipping mask
  LH.urban.clipping.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/LH.urban.clipping.mask.tif"))
    LH.urban.clipping.mask[!is.na(LH.urban.clipping.mask)] <- 0

# open species list
  protected.species <- read.csv(paste0(computer,"/GIS_data/Hunter/species point data/IBRA threatened species list.csv"))
    levels(protected.species$LH.sdm) <- c(NA,"SDM","SSI")

# open tec list
  tec.data <- read.csv(paste0(computer,"/GIS_data/Hunter/species point data/GreaterHunter_DRAFT_100812 (2).csv"))
    tec.data$LH.points <- NA
    tec.data$LH.sdm <- NA

# delete all existing tifs in lower hunter folder
## only run this if you definitely want to delete these files!!
tifs <- dir(paste0(LH.zonation.dir,"extant/"), pattern="LH.tif$",full.names=T)
# file.remove(tifs)
tifs <- dir(paste0(LH.zonation.dir,"pre1750/"), pattern="LH.tif$",full.names=T)
# file.remove(tifs)

maxent.summary <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/all_variables/output/DotE report - maxent summary.csv"))

poorly.modelled <- read.csv(paste0(maxent.dir,"DotE report - poorly modelled species.csv"))

```

```{r presence.absence.raster function}
    
presence.absence.raster <- function (mask.raster,species.data,raster.label="") {
    #set the cells that contain points to 1
  speciesRaster <- rasterize(species.data,mask.raster,field=1)
    if(cellStats(speciesRaster,max)>0){
    speciesRaster <- mask(merge(speciesRaster,mask.raster),mask.raster)
    #label the raster
    names(speciesRaster) <- raster.label
    writeRaster(speciesRaster,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/extant_May2015/",raster.label,"_SSI.LH.tif"), format="GTiff",overwrite=T)
  cat("Converted",as.character(raster.label),"to raster","\n")
  }
  gc()
}

```

Clip species

```{r identify maxent species within LHSA}
# import maxent point data for GH data
  maxent.data <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/species_data/maxent.data_ALA.NSW.csv"))

# create list of unique MaxEnt species
  me.species <- data.frame(species=as.character(unique(maxent.summary$Species)),AUC=NA,in.GH=NA,in.LHSA=NA,GH.max=NA,LH.max=NA)
    

# loop through each species, identify which has points in LHSA and return list
  for(i in seq(me.species$species)){
    s <- maxent.data[as.character(maxent.data$species)==me.species$species[i],]
    
    # identify points within region
    me.species$AUC[i] <- maxent.summary$Test.AUC[grepl(me.species$species[i],maxent.summary$Species)]
    me.species$in.GH[i] <- nrow(s)
    in.LHSA <- length(which(!is.na(extract(LH.clipping.mask,s[,c("easting","northing")]))))
    
    
    if(in.LHSA>0) {
      me.species$in.LHSA[i] <- "TRUE"
      cat(as.character(me.species$species[i]),"has", in.LHSA, "points in LHSA","\n")
      protected.species$lower.hunter[protected.species$Scientific.Name==as.character(me.species$species[i])] <- in.LHSA
        } else me.species$in.LHSA[i] <- "FALSE"
  }

```

```{r clip maxent output for species with points in LHSA}

# create list of LHSA species to clip
  LH.tifs <- me.species$species[me.species$in.LHSA == TRUE & me.species$AUC>=0.7]
    LH.tifs <- gsub(" ","_",LH.tifs)

# function to clip to LHSA region
  clip.to.LH <- function(tiff, mask.raster){
    r <- raster(paste0(GH_PM.zonation.dir,"extant/",tiff,"_SDM.GH_PM.tif"),crs=GDA94.56)
    
    if( cellStats(r,max) > 1){
      r <- mask(crop(r,mask.raster),mask.raster,filename=paste0(LH.zonation.dir,"extant_May2015/",tiff,"_SDM.LH.tif"),overwrite=T)
      cat("Clipped",as.character(tiff),"to Lower Hunter","\n")}
      
  }

  for(j in seq(LH.tifs)){  
    species <- LH.tifs[j] 
      species <- gsub("_"," ",species)  
    
    tryCatch({
      clip.to.LH(LH.tifs[j],LH.clipping.mask)
      me.species[me.species$species==as.character(species),"GH.max"] <- cellStats(raster(paste0(GH_PM.zonation.dir,"extant/",LH.tifs[j],"_SDM.GH_PM.tif"),crs=GDA94.56),max)/1000
      me.species[me.species$species==as.character(species),"LH.max"] <- cellStats(raster(paste0(LH.zonation.dir,"extant_May2015/",LH.tifs[j],"_SDM.LH.tif"),crs=GDA94.56),max)/1000
      
      if(me.species[me.species$species==as.character(species),"LH.max"]*1000 > 1){
        protected.species$LH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SDM"
      }
    }, error=function(err) cat(""),warning=function(war) cat("Check",LH.tifs[j],"for missing tif","\n"))
  }

# save species list output for future use
  write.csv(me.species,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/maxent_species.list.csv"),row.names=F)


# for(i in seq(me.species$species)){
#   protected.species$greater.hunter[grepl(me.species$species[i],protected.species$Scientific.Name,fixed=T)] <- me.species$in.GH[me.species$species==me.species$species[i]]
#   protected.species$GH.sdm[grepl(me.species$species[i],protected.species$Scientific.Name)] <- "SDM"
# }
```

```{r identify species with low AUC scores in LH and convert to SSI}
me.species <- read.csv(paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/maxent_species.list.csv"))

# set minimum threshold
  threshold <- 0.7

# identify species that have low SDM values within the LH
  species.list <- as.character(me.species$species[me.species$LH.max/me.species$GH.max<0.25])
    species.list <- species.list[!is.na(species.list)]
  # add those species that seem to be missing SDMs  
    species.list <- unique(c(as.character(species.list),as.character(me.species$species[me.species$in.LHSA==TRUE & is.na(me.species$GH.max) & me.species$in.GH<100]),as.character(me.species$species[me.species$AUC < threshold & me.species$in.GH<100])))
  
# create presence-absence rasters for species with low AUC values 
    if(length(species.list)>0){
     
      for(i in seq(species.list)){
        species <- gsub(" ","_",species.list[i])
        species.data <- maxent.data[maxent.data$species == species.list[i],]
        species.data <- species.data[,c("easting","northing")]
                presence.absence.raster(LH.clipping.mask,species.data, raster.label=species)
        try({
            file.remove(paste0(LH.zonation.dir,"extant/",species,"_SDM.LH.tif"))
            cat("Removed",paste0(species,"_SDM.LH.tif","\n"))
            },silent=T)
        species <- gsub("_"," ",species)
        protected.species$LH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SSI"
      }
    }

# remove species with poor AUC values & more than 100 points
species.list <- as.character(me.species$species[me.species$AUC < threshold & me.species$in.GH>100])
for(i in seq(species.list)){
try({
            file.remove(paste0(LH.zonation.dir,"extant/",gsub(" ","_",species.list[i]),"_SDM.LH.tif"))
            cat("Removed",paste0(species.list[i],"_SDM.LH.tif","\n"))
            },silent=T)
}

# save species list output for future use
  write.csv(me.species,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/maxent_species.list.csv"),row.names=F)

```


```{r create species SSI tifs}

  ssi.dir <- paste0(computer,"/GIS_data/Hunter/zonation/GH_PM/SSI/")

  ssi.species <- data.frame(species=dir(ssi.dir, pattern=".txt$"),in.GH=NA,in.LHSA=NA)

for(i in seq(ssi.species$species)){
  try({
    species.data <- read.table(paste0(ssi.dir,ssi.species$species[i]),sep="\t")
    colnames(species.data) <- c("easting","northing","V3","V4")
  species <- strsplit(as.character(ssi.species$species[i]),"_GH.PM.txt")
    species <- gsub(" ","_",species)
  
  # identify points within region
    ssi.species$in.GH[i] <- nrow(species.data)
    in.LHSA <- length(which(!is.na(extract(LH.clipping.mask,species.data[,c("easting","northing")]))))
    
    species <- gsub("_"," ",species)
    protected.species$greater.hunter[protected.species$Scientific.Name==as.character(species)] <- nrow(species.data)
    protected.species$GH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SSI"  
  
    if(in.LHSA>0) {
      ssi.species$in.LHSA[i] <- "TRUE"
      cat(as.character(species),"has",in.LHSA,"points in LHSA","\n")
          
      presence.absence.raster(LH.clipping.mask,species.data[,1:2], raster.label=species)
      
      protected.species$LH.sdm[protected.species$Scientific.Name==as.character(species)] <- "SSI"
      protected.species$lower.hunter[protected.species$Scientific.Name==as.character(species)] <- in.LHSA
    
    } else ssi.species$in.LHSA[i] <- "FALSE"
  })
  
  }



write.csv(ssi.species,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/ssi.species.csv"),row.names=F)
# write.csv(protected.species,paste0(computer,"/GIS_data/Hunter/species point data/IBRA threatened species list.csv"),row.names=F)

```


Clip TECS

```{r identify maxent tec within LHSA}
# import maxent point data for GH data
  maxent.data <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/species_data/maxent.data_tecs.csv"))
   maxent.data$tec <- gsub("'",".",maxent.data$tec) 

  maxentResults <- read.csv(paste0(computer,"/GIS_data/Hunter/Maxent_files/ghm.pm/all_variables/output/tecs/pre1750v2/contributions.csv"))
    maxentResults$tec <- gsub("'",".",maxentResults$tec)

# create list of unique MaxEnt tec
  me.tec <- data.frame(tec=unique(maxent.data$tec),in.GH=NA,in.LHSA=NA,GH.max=NA,LH.max=NA,AUC=NA)

# loop through each tec, identify which has points in LHSA and return list
  for(i in seq(me.tec$tec)){
    s <- maxent.data[maxent.data$tec==me.tec$tec[i],]
    
    # identify points within region
    me.tec$in.GH[i] <- nrow(s)
    in.LHSA <- length(which(!is.na(extract(LH.clipping.mask,s[,c("easting","northing")]))))
    
    if(in.LHSA>0) {
      me.tec$in.LHSA[i] <- "TRUE"
      cat(as.character(me.tec$tec[i]),"has", in.LHSA, "points in LHSA","\n")
      tec.data$LH.points[tec.data$TEC_Amy==as.character(me.tec$tec[i])] <- in.LHSA
        } else me.tec$in.LHSA[i] <- "FALSE"
    me.tec$AUC[i] <- maxentResults[grepl(me.tec$tec[i],maxentResults$tec),"cv.roc.mean" ]
  }

```

```{r clip tec maxent output for tec with points in LHSA}
# location of GH files
  tec.dir <- paste0(computer,"/GIS_data/Hunter/zonation/GH_PM/extant/")

# location of LH files
  LH.zonation.dir <- paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/")

# create list of LHSA tec to clip
  LH.tifs <- me.tec$tec[me.tec$in.LHSA == TRUE]
    LH.tifs <- gsub(" ","_",LH.tifs)
    LH.tifs <- gsub("'",".",LH.tifs)

# function to clip to LHSA region
  clip.to.LH <- function(tiff, mask.raster){
    r <- raster(paste0(tec.dir,tiff,"_SDM.GH_PM.tif"))
    
    if( cellStats(r,max) > 1){
      r <- mask(crop(r,mask.raster),mask.raster,filename=paste0(LH.zonation.dir,"extant_May2015/",tiff,"_SDM.LH.tif"),format="GTiff",overwrite=T)
      cat("Clipped",as.character(tiff),"to Lower Hunter","\n")}
      
  }

  for(j in seq(LH.tifs)){  
    tec <- LH.tifs[j]  
    
    tryCatch({
      clip.to.LH(LH.tifs[j],LH.clipping.mask)
      me.tec[me.tec$tec==tec,"GH.max"] <- cellStats(raster(paste0(tec.dir,LH.tifs[j],"_SDM.GH_PM.tif")),max)/1000
      me.tec[me.tec$tec==tec,"LH.max"] <- cellStats(raster(paste0(LH.zonation.dir,"extant_May2015/",LH.tifs[j],"_SDM.LH.tif")),max)/1000
      
      if(me.tec[me.tec$tec==tec,"LH.max"]*1000 > 1){
        tec.data$LH.sdm[tec.data$TEC_Amy==as.character(tec)] <- "SDM"
      }
    }, error=function(err) cat(""),warning=function(war) cat("Check",LH.tifs[j],"for missing tif","\n"))
  }

# save tec list output for future use
  write.csv(me.tec,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/maxent_tec.list.csv"),row.names=F)

```


```{r identify tec with low AUC scores in LH and convert to SSI}

# # set minimum threshold
  threshold <- 0.7

# identify tec that have low SDM values within the LH
  low.AUC <- me.tec$tec[me.tec$AUC < threshold]
    low.AUC <- as.character(low.AUC[!is.na(low.AUC)])
  low.predictions <- as.character(me.tec$tec[me.tec$LH.max/me.tec$GH.max<0.25])
    low.predictions <- as.character(low.predictions[!is.na(low.predictions)])
  missing.sdms <- as.character(me.tec$tec[me.tec$in.LHSA==TRUE & is.na(me.tec$GH.max)])
  # add those tec that seem to be missing SDMs  
    tec.list <- c(low.AUC,low.predictions,missing.sdms)
  
# create presence-absence rasters for tec with low SDM values 
    if(length(tec.list)>0){
     
      for(i in seq(tec.list)){
        
        ssi.data <- maxent.data[maxent.data$tec == tec.list[i],]
        ssi.data <- ssi.data[,c("easting","northing")]
  
        presence.absence.raster(LH.clipping.mask,ssi.data, raster.label=tec.list[i])
        try({
            file.remove(paste0(LH.zonation.dir,"extant_May2015/",tec.list[i],"_SDM.LH.tif"))
            cat("Removed",paste0(tec.list[i],"_SDM.LH.tif","\n"))
            },silent=T)
        
        tec.data$LH.sdm[tec.data$TEC_Amy==as.character(tec.list[i])] <- "SSI"
      }
    }

# save tec list output for future use
  write.csv(me.tec,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/maxent_tec.list.csv"),row.names=F)

```


```{r create tec SSI tifs}

  ssi.dir <- paste0(computer,"/GIS_data/Hunter/zonation/greater hunter/ssi_files/tecs/")

  ssi.tec <- data.frame(tec=dir(ssi.dir, pattern=".txt$", recursive=T),in.GH=NA,in.LHSA=NA)

for(i in seq(ssi.tec$tec)){  
  ssi.data <- read.table(paste0(ssi.dir,ssi.tec$tec[i]),sep=" ")
    colnames(ssi.data) <- c("easting","northing","V3","V4")
  tec <- tolower(strsplit(as.character(ssi.tec$tec[i]),"_GH.txt"))
  
  # identify points within region
    ssi.tec$in.GH[i] <- nrow(ssi.data)
    in.LHSA <- length(which(!is.na(extract(LH.clipping.mask,ssi.data[,c("easting","northing")]))))
    
    if(in.LHSA>0) {
      ssi.tec$in.LHSA[i] <- "TRUE"
      cat(as.character(tec),"has",in.LHSA,"points in LHSA","\n")
          
      presence.absence.raster(LH.clipping.mask,ssi.data[,c("easting","northing")], raster.label=tec)
      
      tec.data$LH.sdm[tec.data$TEC_Amy==tec] <- "SSI"
      tec.data$LH.points[tec.data$TEC_Amy==tec] <- in.LHSA
    
    } else ssi.tec$in.LHSA[i] <- "FALSE"
  
  }

write.csv(ssi.tec,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/ssi.tec.csv"),row.names=F)

```

```{r clip pre1750 layers}
if (pre1750 == TRUE){

  cat("Clipping pre1750 layers to LHSA","\n")
  
# function to clip to LHSA region
  clip.pre1750.to.LH <- function(tiff, mask.raster){
    r <- raster(paste0(GH_PM.zonation.dir,"pre1750/",tiff),crs=GDA94.56)
    tiff <- gsub(".GH_PM.tif","",tiff)
      r <- mask(crop(r,mask.raster),mask.raster,filename=paste0(LH.zonation.dir,"pre1750_May2015/",tiff,".LH.tif"),format="GTiff",overwrite=T)
      cat("Clipped",as.character(tiff),"to Lower Hunter","\n")
    }      
  
  
sdms <- dir(paste0(LH.zonation.dir,"extant_May2015/"),pattern="_SDM.LH.tif")
  sdms <- gsub("SDM.LH","pre1750_SDM.GH_PM",sdms)
  
    for(i in seq(sdms)){
      try(clip.pre1750.to.LH(sdms[i],LH.urban.clipping.mask),silent=T)
    }
}

# remove species with poor AUC values & more than 100 points
species.list <- gsub(" ","_",as.character(poorly.modelled$Species[poorly.modelled$N.records>100]))
for(i in seq(species.list)){
try({
            file.remove(paste0(LH.zonation.dir,"pre1750/",species.list[i],"_pre1750_SDM.LH.tif"))
            cat("Removed",paste0(species.list[i],"_pre1750_SDM.LH.tif","\n"))
            },silent=T)
}

```


```{r check for rasters of the wrong dimensions}
# cells <- length(LH.clipping.mask[!is.na(LH.clipping.mask)])
# 
# tifs <- dir(LH.zonation.dir, pattern="_LH.tif$",full.names=T,recursive=T)
# 
# errors <- NULL
# 
# steps <- length(tifs)
# bar <- txtProgressBar(min=0,max=steps,style=3)
# 
# for(i in seq(tifs)){
#   
#   setTxtProgressBar(bar,i)
#   
#   r<- raster(tifs[i])
#   # check if the same size
#   if(length(r[!is.na(r)])!= cells) {
#     r <- mask(crop(r,LH.clipping.mask),LH.clipping.mask)
#     # if now the right size and still has data, save raster
#     if(cellStats(r,max)>0 & length(r[!is.na(r)])== cells) {
#       writeRaster(r,paste0(LH.zonation.dir,tifs[i]),overwrite=T)
#     } else errors <- append(errors,tifs[i])
#   }
# }
# 
# close(bar)
# 
# # note that this is a hack as these files still aren't the same size - not sure why
# #sewpac <- c("ghff_foraging_LH.tif","koala_rawhabval6_LH.tif","Regent_Honeyeater_LH.tif","Swift_Parrot_LH.tif")
# #errors <- errors[!errors %in% sewpac]
# 
# ## only run this if you definitely want to delete these files!!
# # file.remove(paste0(LH.zonation.dir,errors))

```


```{r create zonation spp file}
  ignore.species <- gsub(" ","_",protected.species$Scientific.Name[protected.species$ignore=="Y"])

  extant.tifs <- dir(paste0(LH.zonation.dir,"extant_May2015/"), pattern=".LH.tif$")
    extant.tifs <- extant.tifs[!extant.tifs %in% paste0(ignore.species,"_SSI.LH.tif")]
    extant.tifs <- extant.tifs[!extant.tifs %in% paste0(ignore.species,"_SDM.LH.tif")]
    extant.tifs <- extant.tifs[!extant.tifs %in% paste0(ignore.species,"_pre1750_SDM.LH.tif")]
    extant.tifs <- extant.tifs[!grepl("Anthochaera_phrygia|Lathamus_discolor",extant.tifs)]
    extant.tifs <- paste0("extant/",extant.tifs)

  pre1750.tifs <- dir(paste0(LH.zonation.dir,"pre1750_May2015/"), pattern=".LH.tif$")
    pre1750.tifs <- pre1750.tifs[!pre1750.tifs %in% paste0(ignore.species,"_SSI.LH.tif")]
    pre1750.tifs <- pre1750.tifs[!pre1750.tifs %in% paste0(ignore.species,"_SDM.LH.tif")]
    pre1750.tifs <- pre1750.tifs[!pre1750.tifs %in% paste0(ignore.species,"_pre1750_SDM.LH.tif")]
    pre1750.tifs <- paste0("pre1750/",pre1750.tifs)
  
  dote.tifs <- dir(paste0(LH.zonation.dir,"extant_May2015/DotE/"), pattern=".LH.tif$")
      dote.tifs <- paste0("DotE/",dote.tifs)

# combine all features
  tifs <- c(extant.tifs,dote.tifs,pre1750.tifs)
  extant.dote.tifs <- c(extant.tifs,dote.tifs)


LH.extant.zonation.spp <- data.frame(weight=1.0, alpha=1.0, bqp.row=1.0, bqp.buffer=1.0, cell.removal=1.0, species=extant.dote.tifs )
  write.table(LH.extant.zonation.spp,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/LH.extant.zonation_May2015.spp"),sep="\t",row.names=FALSE, col.names=FALSE)

LH.pre1750.zonation.spp <- data.frame(weight=1.0, alpha=1.0, bqp.row=1.0, bqp.buffer=1.0, cell.removal=1.0, species=pre1750.tifs )
  write.table(LH.pre1750.zonation.spp,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/LH.pre1750.zonation_May2015.spp"),sep="\t",row.names=FALSE, col.names=FALSE)


weights <- protected.species[protected.species$ignore!="Y",c("Scientific.Name","weight")]
temp <- tec.data[!duplicated(tec.data$TEC_Amy),c("TEC_Amy","weight")]
  temp$TEC_Amy <- tolower(temp$TEC_Amy)
  colnames(temp) <- c("Scientific.Name","weight")
weights <- rbind(weights,temp)
  weights$Scientific.Name <- gsub("bioregions","bioregion",gsub(" ","_", weights$Scientific.Name))
  weights <- weights[!is.na(weights$weight),]

#species weights
for(i in seq(LH.extant.zonation.spp$species)){
  try(LH.extant.zonation.spp$weight[i] <- weights$weight[weights$Scientific.Name == gsub("extant|\\/|DotE|\\.LH|\\_LH|\\.tif|\\_SDM|\\_SSI","",LH.extant.zonation.spp$species[i])],silent=T)
}

LH.extant.zonation.spp$weight[is.na(LH.extant.zonation.spp$weight)] <- 1
LH.extant.zonation.spp$weight[grepl("Nominated",LH.extant.zonation.spp$species)] <- 7
LH.extant.zonation.spp$weight[grepl("Regent_Honeyeater",LH.extant.zonation.spp$species)] <- protected.species$weight[grepl("Regent Honeyeater",protected.species$Common.Name)]
LH.extant.zonation.spp$weight[grepl("Swift_Parrot",LH.extant.zonation.spp$species)] <- protected.species$weight[grepl("Swift Parrot",protected.species$Common.Name)]
LH.extant.zonation.spp$weight[grepl("ghff",LH.extant.zonation.spp$species)] <- protected.species$weight[grepl("Grey-headed Flying-fox",protected.species$Common.Name)]
LH.extant.zonation.spp$weight[grepl("koala",LH.extant.zonation.spp$species)] <- protected.species$weight[grepl("Koala",protected.species$Common.Name)]

write.table(LH.extant.zonation.spp,paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/LH.extant.zonation.weighted_May2015.spp"),sep="\t",row.names=FALSE, col.names=FALSE)

write.csv(protected.species,paste0(computer,"/GIS_data/Hunter/species point data/IBRA threatened species list.csv"),row.names=F)

write.csv(tec.data,paste0(computer,"/GIS_data/Hunter/species point data/GreaterHunter_DRAFT_100812 (2).csv"),row.names=F)


# file.remove(paste0(LH.zonation.dir,"extant/",gsub(" SDM","_SSI",gsub("_"," ",extant.tifs[duplicated(strip.names(extant.tifs))]))))
# file.rename(paste0(LH.zonation.dir,"extant/",extant.tifs),paste0(LH.zonation.dir,"extant/",gsub(" ","_",extant.tifs)))
```
