Prepare species layers provided by SEWPAC for inclusion in Zonation
========================================================

This script takes the [four species datasets provided by SEWPAC](file:///C:/Users/awhitehead/Documents/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research) and converts them to a format that can be used in Zonation.  The species are:
* Swift parrot
* Regent Honeyeater
* Koala
* Grey-headed flying fox

```{r load_data}
rm(list=ls())
library(raster)
library(rgdal)
library(maptools)
library(rgeos)

computer <- "H:/UM backup/"
# computer <- "Z:/Amy/"
# computer <- "//654cw-20990/Amy"

  zonation.dir <- c(paste0(computer,"/GIS_data/Hunter/zonation/lower hunter/"))

  GDA94.56 <- CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  GDA94 <- CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

  LH.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/LH.mask.tif"))
  LH.mask[!is.na(LH.mask)] <- 0

  LH.clipping.mask <- raster(paste0(computer,"/GIS_data/Hunter/mask files/LH.clipping.mask_v2.tif"))
    # set the background cells in the raster to 0
    LH.clipping.mask[!is.na(LH.clipping.mask)] <- 0


convert.to.tif <- function (r, rescale=1) {
  if(projection(r) != projection(LH.mask)){
    r <- projectRaster(r,LH.mask)
  }
  
  r <- mask(resample(r, LH.mask),LH.clipping.mask)
  
  species <- names(r)
  if(rescale>1) r <- round(r*rescale,0)
  
  plot(r,main=species)
  
  cat("converted",species, "to tif","\n")
  writeRaster(r,paste0(zonation.dir,"DotE/",species,"_LH.tif"), overwrite=T, format="GTiff")
  return(r)
  
}
```

```{r regent honeyeater}

rh <- raster(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/SPRH/data/LHPP_SPWA&REHO_project_data/REHO Maxent/Regent_Honeyeater.asc"))
  # fill gaps in original raster
  rh[is.na(rh)] <- 0

 rh_lh <- convert.to.tif(rh, rescale=1000)

```

```{r swift parrot}
  swp <- raster(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/SPRH/data/LHPP_SPWA&REHO_project_data/SWPA Maxent/Swift_Parrot.asc"))
  swp[is.na(swp)] <- 0
  swp_lh <- convert.to.tif(swp, rescale=1000)

```

```{r koala}
 koala <- raster(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/Koala/data/commondata/data1/rawhabval6"))
  koala[is.na(koala)] <- 0
  names(koala) <- "koala_rawhabval6"

  koala_lh <- convert.to.tif(koala)

```

Only run the ghff if absolutely necessary as it takes ages!
```{r grey-headed flying fox}
  
## convert ghff foraging habitat to raster  
ghff_foraging <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/GHFF/data/ForagingRanks_Eby_GeoLINK_08012013.shp"), proj4=GDA94.56)

  #flip the rank scaling so that 4 has the highest value
  ghff_foraging$final_rank <- (ghff_foraging$final_rank*-1)+5
    ghff_foraging$final_rank[ghff_foraging$final_rank==5] <- 0.01

  ghff_for <- rasterize(ghff_foraging,LH.mask, field="final_rank")
    ghff_for[is.na(ghff_for)] <- 0

  names(ghff_for) <- "ghff_foraging"

  ghff_for_lh <- convert.to.tif(ghff_for)


## convert ghff roosting habitat camps to raster
  ghff_roosting <- readShapePoints(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/GHFF/data/LH_GHFFcamps_GeoLINK_Eby_05042013.shp"), proj4=GDA94.56)
  
  # add the estimated habitat availability for each camp from Table 5.1 from report
  ghff_roosting$area_ha <- c(6,10,0.7,10,10,10,10,10,10,0.25,0.25,10,10,10,10,2,10,10,4,4)

  # buffer each camp to give the approximate area in hectares as specified in the report (Table 5.1)
  ghff_roost_buff <- gBuffer(ghff_roosting,byid=TRUE,id=ghff_roosting$Name, sqrt(ghff_roosting$area_ha*10000 / pi))

  ghff_roost_rast <- rasterize(ghff_roost_buff,LH.mask,field=1)

  names(ghff_roost_rast) <- "ghff_roosting"
  ghff_roost_rast[is.na(ghff_roost_rast)] <- 0

  ghff_roost_lh <- convert.to.tif(ghff_roost_rast)

```

Ecological Communities

```{r convert to raster function}
create.raster <- function (s, mask.raster, raster.label, value=1, transform=FALSE) {
    
   if(transform==TRUE) {
     proj4string(s) <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
    s <- spTransform(s, CRS("+proj=utm +zone=56 +south +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
     }
    
  r <- rasterize(s,mask.raster)
    r[!is.na(r)] <- value
    r <- mask(merge(r,mask.raster),mask.raster, filename=paste0(zonation.dir,"DoTE/",raster.label), format="GTiff", overwrite=T)
    names(r) <- rep(raster.label,length(names(r)))
    
    plot(r, main=raster.label,legend=F,axes=F)

    return(r)
  }

```

```{r saltmarsh}

saltmarsh <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/EC/data/LH_Nominated_EC_Saltmarsh.shp"), proj4=GDA94)

saltmarsh.raster <- create.raster(saltmarsh,LH.clipping.mask,raster.label="Nominated_EC_Saltmarsh_LH",transform=T)

```

```{r hinterland}

hinterland <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/EC/data/LH_Nominated_EC_Hinterland.shp"), proj4=GDA94)

hinterland.raster <- create.raster(hinterland,LH.clipping.mask,raster.label="Nominated_EC_Hinterland_LH",transform=T)

```

```{r lowland}

lowland <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/EC/data/LH_Nominated_EC_Lowland.shp"), proj4=GDA94)

lowland.raster <- create.raster(lowland,LH.clipping.mask,raster.label="Nominated_EC_Lowland_LH",transform=T)

```

```{r Littoral}

littoral <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/EC/data/LH_Nominated_EC_Littoral.shp"), proj4=GDA94)

littoral.raster <- create.raster(littoral,LH.clipping.mask,raster.label="Nominated_EC_Littoral_LH",transform=T)

```

```{r remnant}

remnant <- readShapePoly(paste0(computer,"/GIS_data/Hunter/All data from harddrive/From DO/LH_DoE_research/SEWPAC/EC/data/LH_Nominated_EC_Remnant.shp"), proj4=GDA94)

remnant1.raster <- create.raster(remnant[grepl("Yes, map unit specified in nomination",remnant$IN_NOMINAT),],LH.clipping.mask,raster.label="remnant1",transform=T, value=1)

remnant05.raster <- create.raster(remnant[grepl("No, but consistent with community definiton",remnant$IN_NOMINAT),],LH.clipping.mask,raster.label="remnant05",transform=T, value=0.5)

remnant.raster <- max(stack(remnant1.raster,remnant05.raster))
names(remnant.raster) <- "Nominated_EC_Remnant"

convert.to.tif(remnant.raster)

```